# Setup {-}

This section describes the setup procedure.

## Authentication {-}

The data are stored in an account on <https://kf.kobotoolbox.org>. 
The login credentials for that account are shared among the PLAY Project staff. 
To access the site's API programmatically, an API key was downloaded and added to the local `~/.Renviron` file.

<!-- https://bookdown.org/yihui/bookdown/html.html#callout-blocks -->
<!--Available blocks are: .rmdnote, .rmdcaution, .rmdimportant, .rmdtip, and .rmdwarning -->
::: {.rmdimportant}
The KoBoToolBox API key is **not** synched to GitHub.
:::


## Set-up {-}

To test whether the local system has the API key installed, run the command `Sys.getenv("KOBO_API_KEY")`. 

### Check KoBo API Key{-}

```{r check-api-key}
kb_api <- Sys.getenv("KOBO_API_KEY")
if ((length(kb_api) != 1) || (!is.character(kb_api))) {
  stop("'KOBO_API_KEY' not installed in .Renviron")
} else {
  message("'KOBO_API_KEY' installed.")
}
```

### Load/source helper functions {-}

::: {.rmdnote}
The following blocks are not evaluated because of the move to the `{targets}` package
and the use of the `renv` package.
The instructions should be updated.
:::

With the API key installed, several custom functions in `R/kobo_export.R` can be run.

```{r source-helpers, eval=FALSE}
if (file.exists("R/kobo_export.R")) {
  source(file.path("R/kobo_export.R"))
} else {
  stop("File not found: 'R/kobo_export.R'")
}
```

### Install dependencies {-}

The helper functions require several external packages. To confirm that these are installed, run the following chunk.

```{r install-dependencies, eval=FALSE}
if (params$install_deps) {
  install_kobo_packages()  
} else {
  message("'params$install_deps' is FALSE, so no dependencies are installed.")
}
```
