---
title: "Add Databrary info to CSVs"
subtitle: "Version `r Sys.time()`"
author: Rick Gilmore
output: 
  html_document:
    code_folding: show
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  csv_input_dir: 'csv/release_1.0/identifiers_removed'
  csv_save_dir: 'csv/release_1.0/aggregate'
  no_db_fn: 'PLAY_non_mbcdi_all.csv'
  with_db_fn: 'PLAY_non_mbcdi_all_databrary.csv'
  merge_db_info: true
  databrary_login: 'youremail@yourdomain.com'
  last_col: 265
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document imports non-MB-CDI questions, from which identifiers have been removed, given age group, and language group, aggregates them across age group, language group, and form, and saves the aggregated file to a new `../aggregate` directory. 

By default, the document presumes that we want to convert **all** of the CSV files that meet the `params$form_years`, `params$age_grps`, and `params$lang_grps` constraints found in `params$csv_input_dir` to pairs of properly named CSVs and save them in `params$csv_save_dir`.

The document automatically retrieves matching information from Databrary if `params$merge_db_info` is `TRUE`, the default. This merged file is also seved to the `../aggregate` directory with the filename contained in `params$with_db_fn`.

To render, run `rmarkdown::render("06-make_aggregate_csv.Rmd", params=list(databrary_login = "<youremail@yourdomain.com>"))`, substituting your actual Databrary log ID (email) for `<youremail@yourdomain.com>`.

# Setup

We source the helper functions in `R/kobo_export.R` and `R/kobo_databrary_integration.R`.

```{r source_helpers}
source("R/kobo_export.R")
source("R/kobo_databrary_integration.R")
```

Authenticate to Databrary.

```{r authenticate_to_databrary}
if (!file.exists('.databrary.RData')) {
  if (params$databrary_login == "email@yourdomain.com") {
    stop('Cannot login to Databrary with login id: `', params$databrary_login, '`')
  } else {
    logged_in_db <- databraryapi::login_db(params$databrary_login)
  }
  if (!logged_in_db) {
    stop('Automatic log in failed. Please log in manually.')
  }
} else {
  logged_in_db = TRUE
}
```

# Merge Databrary info

```{r add-Databrary-metadata}
if (logged_in_db)
create_save_kobo_db_merge_csv(file.path(params$csv_save_dir, params$no_db_fn), file.path(params$csv_save_dir, params$with_db_fn))
```

# Clean-up

## Log-out of Databrary

```{r}
databraryapi::logout_db()
```