---
title: "Gather and Clean KoBoToolbox Data v2"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  kb_dir: '~/Box/PLAY-Project@/PLAY_Questionnaires (temporary)/KBTB Files'
  csv_raw_dir: 'csv/raw'
  my_kobo_login: somelogin
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)  # for pipe '%>%'
library(readxl)     # for cell_cols()
library(koboloadeR)
library(purrr)

source("R/kobo_files.R")
```

# Purpose

This document summarizes the development of an automated workflow for gathering and cleaning [PLAY Project](https://play-project.org) survey data from the [KoBoToolbox](https://www.kobotoolbox.org/) tool.

The basic steps can be summarized as follows:

1. Download data files from KoBoToolbox.

2. Session-level data
  a. Clean session-level data
  b. Export session-level data
  
3. Measure-level data
  a. Extract measure-level data from each session
  b. Clean measure-level data for each session
  c. Export measure-level data
  
# Download data files

We can download files directly using the KoBoToolbox API.

This chunk lists available forms. If we set `update_csv` to `TRUE`, then a CSV will be written to a default 'hidden' directory.

```{r}
play_kb <- list_kobo_datasets(update_csv = FALSE)
```

Let's supplement this with data about the number of submissions to each form.

```{r}
play_kb <- play_kb %>%
  dplyr::select(., title, id, url)

# This returns NULL
n_submissions <- purrr::map(play_kb$id, koboloadeR::kobo_submission_count, kobo_login(params$my_kobo_login))
```

That did not work.
So, let's instead download all of these forms and save them as CSVs in `r params$csv_raw_dir`.

```{r}
# We try one first
kb1 <- kobo_form_url_to_df(play_kb$url[1])
```

Then do en masse.

```{r}
these_forms <- 1:dim(play_kb)[1]

purrr::map(these_forms, save_kobo_forms_csvs)
```

Now, we open them one by one and see how many entries there are.

```{r}
get_kobo_form_size <- function(kobo_fn) {
  if (!is.character(kobo_fn)) {
    stop('`kobo_fn` must be a character string.')
  }
  if (!file.exists(kobo_fn)) {
    stop('File not found: ', kobo_fn)
  }
  df <- readr::read_csv(kobo_fn)
  
  tibble::tibble(kobo_fn, n_rows = dim(df)[1], n_cols = dim(df)[2])
}

kobo_csv_fns <- list.files('csv/raw', '\\.csv', full.names = TRUE)

get_kobo_form_size(kobo_csv_fns[1])
```

That works for one, let's try it for all of the CSVs.

```{r}
kobo_csvs_df <- purrr::map_df(kobo_csv_fns, get_kobo_form_size)
```

From visual inspection, I think the forms with actual entries have `(2020-03-04)` in their names.

```{r}
kobo_csvs_df <- kobo_csvs_df %>%
  dplyr::filter(., stringr::str_detect(kobo_fn, '\\(2020\\-03\\-04\\)'))
```

That trims the relevant list to the following:

```{r}
kobo_csvs_df %>%
  kableExtra::kable(.) %>%
  kableExtra::kable_styling(.,
                            bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::scroll_box(width = "800px", height = "300px")
```

# Export column names

Much of the work in cleaning these files comes from renaming variables.
We also want to provide information about the questions asked so that the renamed variables make sense.
Extracting the column names as data helps solve both problems.

```{r}
extract_save_col_names <- function(kobo_csv_fn,
                                   col_csv_path = 'csv/cols') {
  if (!is.character(kobo_csv_fn)) {
    stop('`kobo_csv_fn` must be a character string.')
  }
  if (!file.exists(kobo_csv_fn)) {
    stop('File not found: ', kobo_csv_fn)
  }
  if (!is.character(col_csv_path)) {
    stop('`col_csv_path` must be a character string.')
  }
  if (!dir.exists(col_csv_path)) {
    stop('Directory not found: ', col_csv_path)
  }
  
  df <- readr::read_csv(kobo_csv_fn)
  df_names <- names(df)
  
  names_csv_fn <- file.path(col_csv_path, basename(kobo_csv_fn))
  
  cols_df <- tibble::tibble(orig_name = df_names)
  readr::write_csv(cols_df, names_csv_fn)
  message('Saved file: ', names_csv_fn)
}
```

Test one one.

```{r}
extract_save_col_names(kobo_csvs_df$kobo_fn[1])
```

Now, do them all.

```{r}
purrr::map(kobo_csvs_df$kobo_fn, extract_save_col_names)
```

Now, we're cookin' with gas, as my grandad used to say.

The point of this is to create a database about each question that we can then use for cleaning and exporting.
The bonus here is that KoboToolbox does some useful editing of the questions that we can exploit.

# Export raw questions

The CSVs exported by KoBoToolbox do not contain the full text of questions.

```{r}
xlsx_fl <- list.files('~/Box/PLAY-Project@/PLAY_Questionnaires (temporary)/KBTB Files', '\\.xlsx$', full.names = TRUE)
```

Load one.

```{r}
this_xl <- readxl::read_excel(xlsx_fl[1])
```
And save it.

```{r}
these_names <- names(this_xl)
df_names <- tibble::tibble(column_names = these_names)
readr::write_csv(df_names, file.path('csv', 'raw_qs', paste0(basename(xlsx_fl[1]), '.csv')))
```

Turn into a function.

```{r}
extract_save_col_names_from_xlsx <- function(kobo_xlsx_fn,
                                             col_csv_path = 'csv/raw_qs') {
  if (!is.character(kobo_xlsx_fn)) {
    stop('`kobo_xlsx_fn` must be a character string.')
  }
  if (!file.exists(kobo_xlsx_fn)) {
    stop('File not found: ', kobo_xlsx_fn)
  }
  if (!is.character(col_csv_path)) {
    stop('`col_csv_path` must be a character string.')
  }
  if (!dir.exists(col_csv_path)) {
    stop('Directory not found: ', col_csv_path)
  }
  
  df <- readxl::read_excel(kobo_xlsx_fn)
  df_names <- names(df)
  
  names_csv_fn <-
    file.path(col_csv_path, paste0(tools::file_path_sans_ext(basename(kobo_xlsx_fn)), '.csv'))
  
  cols_df <- tibble::tibble(orig_name = df_names)
  readr::write_csv(cols_df, names_csv_fn)
  message('Saved file: ', names_csv_fn)
}
```

Test the function.

```{r}
extract_save_col_names_from_xlsx(xlsx_fl[1])
```

Now run across all files.

```{r}
purrr::map(xlsx_fl, extract_save_col_names_from_xlsx)
```

