# MB-CDI {-}

## Purpose {-}

This page documents the cleaning and merging procedures related to the MB-CDI data.
The home visit workflow strips these files into their own set of CSVs under `data/csv/home_visit/mbcdi`.

The aggregate (across language group and age) data files are saved under `data/csv/agg`.

## Preparation {-}

```{r}
source(file.path(here::here(), "R", "_OLD", "functions.R"))

purrr::walk(list.files(file.path(here::here(), "R"), "\\.R$", full.names = TRUE), source)
```

Let's investigate the number of files, records, and variables per file.

```{r}
mbcdi_fns <-
  list.files(file.path(here::here(), "data", "csv", "home_visit", "mbcdi"), "\\.csv$", full.names = TRUE)

length(mbcdi_fns)
```

```{r make_datafile_summary}
make_datafile_summary <- function(csv) {
  assertthat::is.string(csv)
  assertthat::is.readable(csv)
  
  df <-
    readr::read_csv(csv,
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)
  
  
  
  data.frame(fn = csv,
             age_group = extract_age_group_from_name(csv),
             lang_cond = form_language(csv),
             n_subs = dim(df)[1],
             n_vars = dim(df)[2])
}
```

```{r mbcdi-file-rpt}
mbcdi_file_dat <-
  purrr::map(mbcdi_fns, make_datafile_summary) |> purrr::list_rbind()

mbcdi_file_dat |>
  dplyr::arrange(age_group, lang_cond, n_subs) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_classic()
```

## 12-mo-old English speakers {-}

```{r}
eng_12_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '12', lang_cond == 'english', n_subs > 0)
```

```{r}
eng_12_combined_df <- purrr::map(eng_12_files$fn, mcdi_clean_12_csv) |>
  purrr::list_rbind()
```

```{r}
eng_12_fn <- file.path(here::here(), "data", "csv", "home_visit", "agg", "mcdi_english_12_combined.csv")
readr::write_csv(eng_12_combined_df, eng_12_fn)
```

There are $n=$ `r dim(eng_12_combined_df)[1]` participant records.

## 18-mo-old English speakers {-}

::: {.rmdnote}

This code should be wrapped in functions since many of the components duplicate one another.

:::

```{r}
eng_18_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '18', lang_cond == 'english', n_subs > 0)
```

```{r}
eng_18_combined_df <- purrr::map(eng_18_files$fn, mcdi_clean_18_24_csv) |>
  purrr::list_rbind()
```

```{r}
eng_18_fn <- file.path(here::here(), "data", "csv", "home_visit", "agg", "mcdi_english_18_combined.csv")
readr::write_csv(eng_18_combined_df, eng_18_fn)
```

There are $n=$ `r dim(eng_18_combined_df)[1]` participant records.

## 24-mo-old English speakers {-}

```{r}
eng_24_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '24', lang_cond == 'english', n_subs > 0)
```

```{r}
eng_24_combined_df <- purrr::map(eng_24_files$fn, mcdi_clean_18_24_csv) |>
  purrr::list_rbind()
```

```{r}
eng_24_fn <- file.path(here::here(), "data", "csv", "home_visit", "agg", "mcdi_english_24_combined.csv")
readr::write_csv(eng_24_combined_df, eng_24_fn)
```

There are $n=$ `r dim(eng_18_combined_df)[1]` participant records.

## Old code {-}

::: {.rmdnote}

The following code is deprecated as of 2023-10-25, and is _not_ run.

:::

For simplicity, we'll start with the youngest age group, and with the English speakers.
There are $n=3$ forms, with 4, 10, and 111 participants each, and 254, 253, and 257 variables.

```{r, eval=FALSE}
eng_12_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '12', lang_cond == 'english', n_subs > 0)
```

We'll examine the first one.

```{r, eval=FALSE}
eng_12_331 <- readr::read_csv(eng_12_files$fn[1],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_331) |> head()
```

Let's try trimming the metadata labels.

```{r, eval=FALSE}
eng_12_331_trim_names <- 
  names(eng_12_331) |> basename()

eng_12_331_trim_names |> head()
```

That looks better.
Let's look at the second file.

```{r, eval=FALSE}
eng_12_363 <- readr::read_csv(eng_12_files$fn[2],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_363) |> basename() |> head()
```

And the third one.

```{r, eval=FALSE}
eng_12_740625 <- readr::read_csv(eng_12_files$fn[3],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_740625) |> basename() |> head()
```

Now, we'll create a function to clean the variable names.

```{r, eval=FALSE}
select_basename <- function(csv_fn) {
  assertthat::is.string(csv_fn)
  assertthat::is.readable(csv_fn)
  
  df <- readr::read_csv(csv_fn,
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)
  
  names(df) <- basename(names(df))
  df
}
```

```{r, eval=FALSE}
select_basename(eng_12_files$fn[3]) |> head()
```

Let's trim unneeded fields.
We'll write several helper functions to do this.

```{r, eval=FALSE}
trim_cdi_fields <- function(df) {
  df |>
    dplyr::select(-contains("note"),
                  -contains("instructions"),
                  -contains("comments"),
                  -contains("continue"),
                  -contains("vocab"),
                  -contains("mcdi"))
}

add_particip_index <- function(df) {
  df |> 
    dplyr::mutate(play_i = 1:dim(df)[1])
}

make_cdi_longer <- function(df) {
  n_vars <- dim(df)[2]
  df |>
    tidyr::pivot_longer(cols = 2:n_vars,
                        names_to = "word",
                        values_to = "understands_or_says") |>
    dplyr::filter(!is.na(understands_or_says)) |>
    dplyr::mutate(understands_or_says = stringr::str_replace(understands_or_says, "understands___", "says")) |>
    dplyr::mutate(
      understands_or_says = stringr::str_replace(understands_or_says, "understands_says", "says")) |>
    dplyr::mutate(word = stringr::str_replace(word, "mommy_001", "mommy")) |>
    dplyr::mutate(word = stringr::str_replace(word, "bath_001", "bath"))
}
```

Then we combine them into an omnibus function.

```{r, eval=FALSE}
clean_cdi <- function(csv_fn) {
  select_basename(csv_fn) |>
    trim_cdi_fields() |>
    dplyr::rename("play_id" = "participant_id") |>
    make_cdi_longer() |>
    add_particip_index()
}
```

Now, we can run `clean_cdi()` across all three files.

```{r, eval=FALSE}
eng_12 <- purrr::map(eng_12_files$fn, clean_cdi) |>
  purrr::list_rbind()
```

```{r, eval=FALSE}
xtabs(~ word + understands_or_says, eng_12)
```

## 18-mo-old English speakers {-}

Let's move on to the 18-mo-old English speakers.

```{r, eval=FALSE}
eng_18_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '18', lang_cond == 'english', n_subs > 0)
```

There are $n=$ `r dim(eng_18_files)[1]` files with participant data.

```{r, eval=FALSE}
clean_cdi(eng_18_files$fn[1])
clean_cdi(eng_18_files$fn[2])
clean_cdi(eng_18_files$fn[3])
```

There are some duplicate entries for some words.

::: {.rmdnote}

~~We need a strategy for reconciling these duplicates: `candy`, `leg`, `rain`, `wet`.~~

It's not elegant, but I have one for modifying the duplicate names. See below.

:::

## 24-mo-old English speakers {-}

Let's move on to the 24-mo-old English speakers.

```{r, eval=FALSE}
eng_24_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '24', lang_cond == 'english', n_subs > 0)
```

There are $n=$ `r dim(eng_24_files)[1]` files with participant data.

Let's see how the `clean_cdi()` works on one of these.

```{r, eval=FALSE}
clean_cdi(eng_24_files$fn[1])
```

Once again, we have duplicates for several items: 'candy', 'leg', 'rain', 'wet'.

It's very hacky, but I think we might want to modify these item names until we figure out a better way to handle the duplicates.

```{r, eval=FALSE}
modify_mcdi_dupes <- function(df, dupe = 'leg') {
  dup_index <- seq_along(df)[names(df) == dupe]
  for (i in 1:length(dup_index)) {
    this_dup <- dup_index[i]
    names(df)[this_dup] <- paste0(dupe, "_", i)
  }
  df
}

open_csv <- function(csv_fn) {
  assertthat::is.string(csv_fn)
  assertthat::is.readable(csv_fn)
  
  df <- readr::read_csv(csv_fn,
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)
}

trim_cdi_18_24_fields <- function(df) {
  df |>
    dplyr::select(-contains("note"),
                  -contains("instructions"),
                  -contains("comments"),
                  -contains("continue"),
                  -contains("vocab"),
                  -contains("mcdi"))
}

make_cdi_18_24_longer <- function(df) {
  n_vars <- dim(df)[2]
  df |>
    tidyr::pivot_longer(cols = 2:n_vars,
                        names_to = "word",
                        values_to = "knows")
 }

clean_cdi_18_24_dedupe <- function(csv_fn) {
  df <- open_csv(csv_fn)
  names(df) <- basename(names(df))
  
  df |>
    modify_mcdi_dupes(dupe = 'leg') |>
    modify_mcdi_dupes(dupe = 'candy') |>
    modify_mcdi_dupes(dupe = 'rain') |>
    modify_mcdi_dupes(dupe = 'wet') |>
    trim_cdi_18_24_fields() |>
    dplyr::rename("play_id" = "participant_id") |>
    make_cdi_18_24_longer()
}
```

```{r, eval=FALSE}
eng_24 <- purrr::map(eng_24_files$fn, clean_cdi_18_24_dedupe) |>
  purrr::list_rbind()
xtabs(~ word + knows, eng_24)
```

Now, we can return to the 18-mo-old data to see if this works:

```{r, eval=FALSE}
eng_18 <- purrr::map(eng_18_files$fn, clean_cdi_18_24_dedupe) |>
  purrr::list_rbind()
xtabs(~ word + knows, eng_18)
```

It does.
