# Screening call {-}

## Collection protocol {-}

Details about the data collection [protocol for participant screening and recruiting](https://www.play-project.org/collection.html#Participant_Recruitment) can be found on the [PLAY Project website](https://play-project.org).

## Retrieve files from KoBoToolbox {-}

The relevant KoBoToolbox data files have 'Demographic Questionnaire' in the title.

```{r list-kobo-forms}
kb_df <- list_kobo_data()
if ((dim(kb_df)[1] < 1) || (!is.data.frame(kb_df))) {
  stop("Error in selecting surveys from KoBoToolbox.")
}

# Restrict to surveys collected at home
kb_demog <- kb_df %>%
  dplyr::filter(., stringr::str_detect(title, "Demographic"))

if ((dim(kb_demog)[1] < 1) || (!is.data.frame(kb_demog))) {
  stop("Error in selecting demographics surveys from KoBoToolbox.")
}
```

### Save selected raw files to local directory {-}

Prepare to retrieve all demographic data files.

```{r}
if (!dir.exists('data/xlsx/screening')) {
  stop("Directory not found: 'data/xlsx/screening'")
}
n_files <- dim(kb_demog)[1]
```

```{r download-demog}
purrr::map(1:n_files, retrieve_save_xls_export, kb_df = kb_demog, save_dir = "data/xlsx/screening")
```

## Convert to CSVs {-}

By default, we presume that we want to convert **all** of the XLSX files in `data/xlxs/screening` to CSVs.

### Open file(s) and process {-}

While not strictly necessary, we filter the downloaded filename to ensure that it includes 'Demographic_Questionnaire'.
The leading 6-digit integer is a unique 'form' identifier, so we extract it.

```{r}
demog_fns <- list.files(file.path("data/xlsx/screening"), pattern = "Demographic_Questionnaire", full.names = TRUE)

demog_fns_trimmed <- basename(stringr::str_replace(demog_fns, pattern = "\\.xlsx", replacement = "\\.csv"))

form_ids <- stringr::str_extract(demog_fns_trimmed, pattern = "[0-9]{6}")
```

Create a helper function to handle import, renaming, and exporting.

```{r}
load_xlsx_save_csv <- function(i, fl) {
  xl <- readxl::read_xlsx(fl[i])
  fn_csv <- stringr::str_replace(fl[i], pattern = "\\.xlsx", replacement = "\\.csv")
  fn_csv <- stringr::str_replace(fn_csv, pattern = "/xlsx/", "/csv/")
  if (dir.exists(dirname(fn_csv))) {
    readr::write_csv(xl, fn_csv)    
  } else {
    warning("Directory not found: '", dirname(fn_csv), "'")
  }
}
```

Import xlsx and save csv version.

```{r}
purrr::map(1:length(demog_fns), load_xlsx_save_csv, demog_fns)
```


## Merge files {-}

### Compare the files {-}

Before merging, we have to examine how the fields compare.

```{r}
csv_fns <- list.files("data/csv/screening", pattern = "\\.csv", full.names = TRUE)
```

Open the first file: '`r basename(csv_fns[1])`'.

```{r}
demog_1 <- readr::read_csv(csv_fns[1], show_col_types = FALSE)
```

There are $n=$ `r dim(demog_1)[1]` data records and $n=$ `r dim(demog_1)[2]` fields.

Open the second file: '`r basename(csv_fns[2])`'.

```{r}
demog_2 <- readr::read_csv(csv_fns[2], show_col_types = FALSE)
```

There are $n=$ `r dim(demog_2)[1]` data records and $n=$ `r dim(demog_2)[2]` fields.

Open the third file: '`r basename(csv_fns[3])`'.

```{r}
demog_3 <- readr::read_csv(csv_fns[3], show_col_types = FALSE)
```

There are $n=$ `r dim(demog_3)[1]` data records and $n=$ `r dim(demog_3)[2]` fields.

::: {.rmdnote}
These files have different numbers of columns, so we will need to be careful in creating a merged data file.
:::

### Extract column names {-}

```{r}
demog_1_names <- names(demog_1)
demog_2_names <- names(demog_2)
demog_3_names <- names(demog_3)
```

Compare 1 to 2.

```{r}
sum(demog_1_names == demog_2_names)
```

Compare 1 to 3.

```{r}
sum(demog_1_names == demog_3_names)
```

Compare 2 to 3.

```{r}
sum(demog_2_names == demog_3_names)
```

The second and third data files have the most overlap.