---
title: "Save raw demographic CSVs"
subtitle: "Version `r Sys.time()`"
author: Rick Gilmore
output: 
  html_document:
    code_folding: show
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  xlsx_download_dir: 'data/xlsx/release_1.0'
  demog_eng_pre_2020: '275882_PLAY_Demographic_Questionnaire.xlsx'
  demog_eng_post_2020: '359546_PLAY_Demographic_Questionnaire.xlsx'
  demog_span: '334134_PLAY_Demographic_Questionnaire_Spanish.xlsx'
  csv_save_dir: 'data/csv/release_1.0/raw'
  path_to_root_dir: '..'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document converts the downloaded 'raw' XLSX files from KoBoToolbox and converts them to CSVs for further processing.

By default, the document presumes that we want to convert **all** of the XLSX files that meet the `params$form_years`, `params$age_grps`, and `params$lang_grps` constraints found in `params$xlsx_download_dir` to CSVs and save them in `params$csv_save_dir`.

# Setup

We source the helper functions in `R/kobo_export.R`.

```{r source_helpers}
source(file.path(params$path_to_root_dir, "R", "kobo_export.R"))
```

# Open file(s) and process

```{r eval=FALSE}
demog_fns <- list.files(file.path(params$path_to_root_dir, params$xlsx_download_dir), pattern = "Demographic_Questionnaire", full.names = TRUE)

form_ids <- stringr::str_extract(demog_fns, "[0-9]{6}")
```

```{r import-xlsx}
demog_eng_pre_2020 <-
  readxl::read_excel(
    file.path(
      params$path_to_root_dir,
      params$xlsx_download_dir,
      params$demog_eng_pre_2020
    )
  )
demog_eng_post_2020 <-
  readxl::read_excel(
    file.path(
      params$path_to_root_dir,
      params$xlsx_download_dir,
      params$demog_eng_post_2020
    )
  )
demog_span <-
  readxl::read_excel(file.path(
    params$path_to_root_dir,
    params$xlsx_download_dir,
    params$demog_span
  ))
```

# Save CSVs

```{r}
readr::write_csv(
  demog_eng_pre_2020,
  file.path(
    params$path_to_root_dir,
    params$csv_save_dir,
    '275882_raw_demog_eng_pre_2020.csv'
  )
)
readr::write_csv(
  demog_eng_post_2020,
  file.path(
    params$path_to_root_dir,
    params$csv_save_dir,
    '359546_raw_demog_eng_post_2020.csv'
  )
)
readr::write_csv(
  demog_span,
  file.path(
    params$path_to_root_dir,
    params$csv_save_dir,
    '334134_raw_demog_span.csv'
  )
)
```
