---
title: "Gather and Clean KoBoToolbox Data"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  kb_dir: '~/Box/PLAY-Project@/PLAY_Questionnaires (temporary)/KBTB Files'
  demog_csv_fn: 'csv/PLAY_demog_clean_all.csv'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)  # for pipe '%>%'
library(readxl)     # for cell_cols()
```

# Purpose

This document summarizes the development of an automated workflow for gathering and cleaning [PLAY Project](https://play-project.org) survey data from the [KoBoToolbox](https://www.kobotoolbox.org/) tool.

The basic steps can be summarized as follows:

1. Download data files from KoBoToolbox

2. Session-level data
  a. Clean session-level data
  b. Export session-level data
  
3. Measure-level data
  a. Extract measure-level data from each session
  b. Clean measure-level data for each session
  c. Export measure-level data

For the time being, we will take already-downloaded data from the PLAY Project Box folder, thereby skipping 1, and we will focus on tasks 2a and 2b. 
We will also defer work on Task 3.

# Gather data

KoBoToolbox data are stored in a private Box folder shared only with the PLAY Project team. 
The folder URL is `https://psu.app.box.com/folder/129677673243`.

This is a list of the files in the PLAY Box folder `(`r params$kb_dir`)`:

```{r}
list.files(params$kb_dir)
```

# Screening data

## Import

Screening questions asked during the initial phone call are pushed via the KoBoToolbox form with a name beginning `PLAY_Demographic_Questionnaire_2020-03-04...`

We will have to handle the case where there are more than one of these files in the target directory.
For now, let's import this one: `PLAY_Demographic_Questionnaire_2020-03-04_-_all_versions_-_labels_-_2021-01-14-19-02-27.xlsx`.

```{r}
demog_fn_short <- 'PLAY_Demographic_Questionnaire_2020-03-04_-_all_versions_-_labels_-_2021-01-15-14-35-07.xlsx'
demog_fn_full <- paste0(params$kb_dir, "/", demog_fn_short)
demog <- readxl::read_excel(demog_fn_full)
```

## Clean

First, let's rename the columns.

```{r, rename-omit-cols}
omit_cols <- c(5, 7:19, 24, 29:41, 43:44, 64:68, 81, 98:99, 
               105:106, 125:126, 144:145, 149, 153:155, 159, 163:164, 169:170,
               176:177, 189:228)

demog_clean <- demog %>%
  dplyr::rename(., start_time = start,
                end_time = end,
                call_date = c_today,
                last_update = 4,
                # expt_inst = 5,
                recruiter_name = 6,
                # expt_say = 7,
                # family_phone = 8,
                # family_email = 9,
                # address_quest = 10,
                # family_address_1 = 11,
                # family_address_2 = 12,
                # family_city = 13,
                # family_state = 14,
                # expt_check = 15,
                # expt_say = 16,
                # child_first = 17,
                # child_middle = 18,
                # child_last = 19,
                child_dob = 20,
                child_mos_check = 21,
                child_mos_trunc = 22,
                child_weeks_cutoff = 23,
                # skip 24
                child_sex = 25,
                child_birth_city = 26,
                play_site_id = 27,
                site_child_id = 28,
                # skip 29:41
                play_child_id = 42,
                # skip 43:44
                lang_at_home = 45, # should parse,
                eng_at_home = 46,
                span_at_home = 47,
                oth_lang_at_home = 48,
                oth_lang_which = 49,
                lang_mom_to_child = 50,
                eng_mom_to_child = 51,
                span_mom_to_child = 52,
                oth_mom_to_child = 53,
                oth_lang_mom_to_child_which = 54,
                ineligible_mom_lang_continue = 55,
                ineligible_mom_lang_recontact = 56,
                lang_oth_to_child = 57,
                eng_oth_to_child = 58,
                span_oth_to_child = 59,
                oth_oth_to_child = 60, # What languages do other household members...
                any_oth_lang_to_child = 61,
                ineligible_other_lang_continue = 62,
                ineligible_other_lang_recontact = 63,
                # skip 64:68 checks
                know_due_date = 69,
                born_on_term = 70,
                ineligible_notterm_continue = 71,
                ineligible_notterm_recontact = 72,
                ineligible_term_unclear_continue = 73,
                ineligible_term_unclear_recontact = 74,
                child_due_date = 75,
                child_birthage = 76,
                ineligible_preterm_wks_continue = 77,
                ineligible_preterm_wks_recontact = 78,
                birthwt_lbs = 79,
                birthwt_oz = 80,
                # skip 81 bw calculator
                ineligible_birthwt_continue = 82,
                ineligible_birtwt_recontact = 83,
                birth_complications_yes_no = 84,
                birth_complications_specify = 85,
                ineligible_complications_continue = 86,
                ineligible_complications_recontact = 87,
                disability_hearing = 87,
                disability_hearing_specify = 88,
                ineligible_hearing_continue = 89,
                disability_vision = 90,
                disability_vision_specify = 91,
                ineligible_vision_continue = 92,
                illness_injury = 93,
                illness_injury_specify = 94,
                ineligible_illness_injury_continue = 95,
                child_race = 96,
                child_ethnicity = 97,
                # skip 98:99
                time_to_sleep = 100,
                time_to_wake = 101,
                nap_hrs = 102,
                where_sleep = 103,
                where_sleep_specify = 104,
                # skip 105:106
                relations_live_with_child = 107, # Need to parse
                biofather_live_with_child = 108,
                male_partner_live_with_child = 109,
                mother_bio_live_with_child = 110,
                female_partner_live_with_child = 111,
                other_gender_partner_live_with_child = 112,
                grandmother_live_with_child = 113,
                grandfather_live_with_child = 114,
                grgrandmother_live_with_child = 115,
                grgrandfather_live_with_child = 116,
                aunt_live_with_child = 117,
                uncle_live_with_child = 118,
                cousin_live_with_child = 119,
                oth_relative_live_with_child = 120,
                non_relative_live_with_child = 121,
                no_one_else_lives_with_child = 122,
                oth_relative_relation_to_child = 123,
                oth_non_relative_relation_to_child = 124,
                # skip 125:126
                caregiver_dob = 127,
                caregiver_child_biomom = 128,
                caregiver_relation_to_child = 129,
                caregiver_start_care = 130,
                caregiver_childbirth_age = 131,
                caregiver_age_at_childbirth = 132,
                ineligible_caregiver_young_continue = 133,
                caregiver_race = 134,
                caregiver_ethnicity = 135,
                caregiver_country_born = 136,
                caregiver_country_specify = 137,
                caregiver_when_to_us = 138,
                caregiver_highest_grade = 139,
                caregiver_pd_employment = 140,
                caregiver_occupation = 141,
                caregiver_n_jobs = 142,
                caregiver_job_training = 143,
                # skip 144:145
                know_biodad_dob = 146,
                biodad_dob = 147,
                biodad_childbirth_age = 148,
                # skip 149
                ineligible_biodad_young_continue = 150,
                biodad_race = 151,
                biodad_ethnicity = 152,
                # skip 153:155
                know_biomom_dob = 156,
                biomom_dob = 157,
                biomom_childbirth_age = 158,
                # skip 159
                ineligible_biomom_young_continue = 160,
                biomom_race = 161,
                biomom_ethnicity = 162,
                # skip 163:164
                know_partner_dob = 165,
                partner_dob = 166,
                partner_race = 167,
                partner_ethnicity = 168,
                # skip 169:170
                partner_highest_grade = 171,
                partner_pd_employment = 172,
                partner_occupation = 173,
                partner_n_jobs = 174,
                partner_job_training = 175,
                # skip 176:177
                nonparental_childcare = 178,
                childcare_inhome = 179,
                childcare_not_inhome = 180,
                childcare_relative = 181,
                childcare_center = 182,
                childcare_none = 183,
                childcare_location = 184,
                childcare_hrs_per_wk = 185,
                childcare_n_children = 186,
                childcare_age_mos_began = 187,
                childcare_provider_lang = 188
                # skip 189:228
  ) %>%
  # The `play_child_id` field has a "/" character in some entries. The next line fixes that.
  dplyr::mutate(., play_child_id = stringr::str_replace(play_child_id, "/", "|")) %>%
  dplyr::select(., -all_of(omit_cols))
```

## Export aggregate file

Now, let's sort them by data collection site, then export as a CSV.

```{r, sort-export-aggregate}
demog_clean %>%
  dplyr::arrange(., play_site_id, play_child_id, call_date) %>%
  readr::write_csv(., paste0(params$kb_dir, '/', params$demog_csv_fn))
```

## Export session-level files

For each valid row in the data frame, we 

1. Extract session based on its unique date/timestamp.
2. Save the row as a CSV with a name like `PLAY-demog-<play_site_id>-<site_child_id>-<play_child_id>-<call_date>.csv`.

We need the extended information in the file name because sometimes the recruiting call occurs over multiple days.

```{r, load-export-function}
select_session_by_datestamp <- function(this_datestamp, df, 
                                  csv_path = paste0(params$kb_dir, '/csv'), 
                                  export_file = TRUE, return_df = FALSE) {
  # if (!is.character(this_child_id)) {
  #   stop(paste0('`this_child_id` must be a string'))
  # }
  if (!is.data.frame(df)) {
    stop(paste0('`df` must be a data frame' ))
  }
  if (!dir.exists(csv_path)) {
    stop(paste0('Invalid directory: ', csv_path))
  }
  
  this_session <- dplyr::filter(df, start_time == this_datestamp)
  
  if (export_file) {
    if (!is_empty(this_session)) {
      session_fn <- paste0('PLAY-demog-',
                           this_session$play_site_id, "-", 
                           this_session$site_child_id, '-', 
                           this_session$play_child_id, '-',
                           this_session$call_date, ".csv")
      readr::write_csv(this_session, paste0(csv_path, "/", session_fn))
      message(paste0('Saved ', paste0(csv_path, "/", session_fn)))
    } 
  }
  
  if (return_df) {
    this_session    
  }
}

```


```{r}
these_sessions <- unique(demog_clean$start_time)
purrr::map(these_sessions, select_session_by_datestamp, demog_clean)
```

# Questionnaire data

There are three age groups (12, 18, and 24 months), and three different KoBoToolbox forms depending on the family language environment (English, Spanish, English/Spanish bilingual).
So, there are nine (9) KoBoToolbox data forms we need to import.

## Import

Let's start with the 12-mo-old English speakers.

```{r}
eng_12_mo_fn <- 'PLAY_Home_Questionnaires_-_12_English_2020-03-04_-_all_versions_-_labels_-_2021-01-15-15-03-35.xlsx'

qs <- readxl::read_excel(paste0(params$kb_dir, "/", eng_12_mo_fn))
```

## Drop, rename, & clean

### Basic info

```{r}
qs_basic <- readxl::read_excel(paste0(params$kb_dir, "/", 
                                eng_12_mo_fn), range = cell_cols("A:AH"))

qs_basic <- qs_basic %>%
  dplyr::rename(., start_time = 1) %>%
  dplyr::rename(., end_time = 2) %>%
  # skip 3
  # skip 4
  dplyr::rename(., todays_date = 5) %>%
  dplyr::rename(., play_site_id = 6) %>%
  dplyr::rename(., experimenter_name = 7) %>%
  dplyr::rename(., session_date = 8) %>%
  dplyr::rename(., site_child_id = 9) %>%
  # dplyr::rename(., child_first = 10) %>%
  # dplyr::rename(., child_middle = 11) %>%
  # dplyr::rename(., child_last = 12) %>%
  dplyr::rename(., child_dob = 13) %>%
  dplyr::rename(., child_sex = 14) %>%
  dplyr::rename(., child_birth_city = 15) %>%
  # skip 16:28
  dplyr::rename(., play_child_id = 29) %>%
  dplyr::rename(., child_age_grp = 30) %>%
  dplyr::rename(., langs_spoken_to_child = 31) %>%
  dplyr::rename(., eng_to_child = 32) %>%
  dplyr::rename(., span_to_child = 33) %>%
  dplyr::rename(., instr_lang = 34) %>%
  dplyr::select(., 1:2, 5:9, 13:15, 29:34)
```

```{r}
select_visit_by_datestamp <- function(this_datestamp, df, 
                                  csv_path = paste0(params$kb_dir, '/csv'), 
                                  export_file = TRUE, return_df = FALSE) {
  # if (!is.character(this_child_id)) {
  #   stop(paste0('`this_child_id` must be a string'))
  # }
  if (!is.data.frame(df)) {
    stop(paste0('`df` must be a data frame' ))
  }
  if (!dir.exists(csv_path)) {
    stop(paste0('Invalid directory: ', csv_path))
  }
  
  this_session <- dplyr::filter(df, start_time == this_datestamp)
  
  if (export_file) {
    if (!is_empty(this_session)) {
      session_fn <- paste0('PLAY-visit-basic-',
                           this_session$play_site_id, "-", 
                           this_session$site_child_id, '-', 
                           this_session$play_child_id, ".csv")
      readr::write_csv(this_session, paste0(csv_path, "/", session_fn))
      message(paste0('Saved ', paste0(csv_path, "/", session_fn)))
    } 
  }
  
  if (return_df) {
    this_session    
  }
}
```

Write all `PLAY-visit-basic-*` data files.

```{r}
these_sessions <- unique(qs_basic$start_time)
purrr::map(these_sessions, select_visit_by_datestamp, qs_basic)
```

### MB-CDI short form

Columns `AU` to `EF` are MB-CDI short form.
That corresponds to columns 47:??.

```{r}
qs_mbcdi_short <- readxl::read_excel(paste0(params$kb_dir, "/", 
                                eng_12_mo_fn), range = cell_cols("AU:EF"))

```

```{r}
qs_mbcdi_short <- qs %>%
  dplyr::rename(., choo_choo = 47) %>%
  dplyr::rename(., meow = 48) %>%
  dplyr::rename(., ouch = 49) %>%
  dplyr::rename(., uh_oh = 50) %>%
  dplyr::rename(., bird = 51) %>%
  dplyr::rename(., dog = 52) %>%
  dplyr::rename(., duck = 53) %>%
  dplyr::rename(., kitty = 54) %>%
  dplyr::rename(., lion = 55) %>%
  dplyr::rename(., mouse = 56) %>%
  dplyr::rename(., car = 57) %>%
  dplyr::rename(., stroller = 58) %>%
  dplyr::rename(., ball = 59) %>%
  dplyr::rename(., book = 60) %>%
  dplyr::rename(., doll = 61) %>%
  dplyr::rename(., bread = 62) %>%
  dplyr::rename(., candy = 63) %>%
  dplyr::rename(., cereal = 64) %>%
  dplyr::rename(., cookie = 65) %>%
  dplyr::rename(., juice = 66) %>%
  dplyr::rename(., toast = 67) %>%
  dplyr::rename(., hat = 68) %>%
  dplyr::rename(., pants = 69) %>%
  dplyr::rename(., shoe = 70) %>%
  dplyr::rename(., sock = 71) %>%
  dplyr::rename(., eye = 72) %>%
  dplyr::rename(., head = 73) %>%
  dplyr::rename(., leg = 74) %>%
  dplyr::rename(., nose = 75) %>%
  dplyr::rename(., tooth = 76) %>%
  dplyr::rename(., chair = 77) %>%
  dplyr::rename(., couch = 78) %>%
  dplyr::rename(., kitchen = 79) %>%
  dplyr::rename(., table = 80) %>%
  dplyr::rename(., television = 81) %>%
  dplyr::rename(., blanket = 82) %>%
  dplyr::rename(., bottle = 83) %>%
  dplyr::rename(., cup = 84) %>%
  dplyr::rename(., dish = 85) %>%
  dplyr::rename(., lamp = 86) %>%
  dplyr::rename(., radio = 87) %>%
  dplyr::rename(., spoon = 88) %>%
  dplyr::rename(., who = 89) %>%
  dplyr::rename(., away = 90) %>%
  dplyr::rename(., outside_1 = 91) %>%
  dplyr::rename(., flower = 92) %>%
  dplyr::rename(., home = 93) %>%
  dplyr::rename(., moon = 94) %>%
  dplyr::rename(., outside_2 = 95) %>%
  dplyr::rename(., plant = 96) %>%  
  dplyr::rename(., rain = 97) %>%
  dplyr::rename(., rock = 98) %>%
  dplyr::rename(., water = 99) %>%
  dplyr::rename(., babysitter = 100) %>%
  dplyr::rename(., girl = 101) %>%
  dplyr::rename(., grandma = 102) %>%
  dplyr::rename(., mommy = 103) %>%
  dplyr::rename(., bath = 104) %>%  
  dplyr::rename(., dont = 105) %>%
  dplyr::rename(., hi = 106) %>%
  dplyr::rename(., night_night = 107) %>%
  dplyr::rename(., patty_cake = 108) %>%
  dplyr::rename(., please = 109) %>%
  dplyr::rename(., wait = 110) %>%
  dplyr::rename(., `break` = 111) %>%
  dplyr::rename(., feed = 112) %>%
  dplyr::rename(., finish = 113) %>%
  dplyr::rename(., help = 114) %>%
  dplyr::rename(., jump = 115) %>%
  dplyr::rename(., kick = 116) %>%
  dplyr::rename(., kiss = 117) %>%
  dplyr::rename(., push = 118) %>%
  dplyr::rename(., sing = 119) %>%
  dplyr::rename(., smile = 120) %>%
  dplyr::rename(., night = 121) %>%
  dplyr::rename(., today = 122) %>%
  dplyr::rename(., all_gone = 123) %>%
  dplyr::rename(., big = 124) %>%
  dplyr::rename(., broken = 125) %>%
  dplyr::rename(., dark = 126) %>%
  dplyr::rename(., fast = 127) %>%
  dplyr::rename(., hurt = 128) %>%
  dplyr::rename(., pretty = 129) %>%
  dplyr::rename(., soft = 130) %>%  
  dplyr::rename(., I = 131) %>%
  dplyr::rename(., me = 132) %>%
  dplyr::rename(., how = 133) %>%
  dplyr::rename(., other = 134) %>%
  dplyr::rename(., some = 135) %>%
  dplyr::rename(., mbcdi_comments = 136) %>%
  dplyr::select(., 6:9, 47:136)
```

Create function to export MB-CDI short.

```{r}
select_mbcdi_short_by_datestamp <- function(this_datestamp, df, 
                                  csv_path = paste0(params$kb_dir, '/csv'), 
                                  export_file = TRUE, return_df = FALSE) {
  # if (!is.character(this_child_id)) {
  #   stop(paste0('`this_child_id` must be a string'))
  # }
  if (!is.data.frame(df)) {
    stop(paste0('`df` must be a data frame' ))
  }
  if (!dir.exists(csv_path)) {
    stop(paste0('Invalid directory: ', csv_path))
  }
  
  this_session <- dplyr::filter(df, start_time == this_datestamp)
  
  if (export_file) {
    if (!is_empty(this_session)) {
      session_fn <- paste0('PLAY-visit-MBCDI-short-',
                           this_session$play_site_id, "-", 
                           this_session$site_child_id, '-', 
                           this_session$play_child_id, ".csv")
      readr::write_csv(this_session, paste0(csv_path, "/", session_fn))
      message(paste0('Saved ', paste0(csv_path, "/", session_fn)))
    } 
  }
  
  if (return_df) {
    this_session    
  }
}
```

```{r, export-mbcdi-short}
these_sessions <- unique(qs_basic$start_time)
purrr::map(these_sessions, select_mbcdi_short_by_datestamp, qs_basic)
```

### A better way

```{r}
# Could be much better and faster
mbcdi_names <- stringr::str_split(string = names(qs_mbcdi_short), pattern = "/")
mbcdi_names_short <- lapply(mbcdi_names, `[`, 7)

# Now clean anomalous names
mbcdi_names_clean <- mbcdi_names_short %>%
  stringr::str_replace(., " \\([a-z ]+\\)", "") %>% # parenthetical
  stringr::str_replace(., ' ', '_') %>% # spaces
  stringr::str_replace(., "'", "") %>% # apostrophe
  stringr::str_replace(., "...45", "_1") %>% # ellipsis
  stringr::str_replace(., "...49", "_2") %>% # ellipsis
  stringr::str_replace(., "\\([a-z ]+\\)", "") # parenthetical

names(qs_mbcdi_short) <- mbcdi_names_clean
```

### DLL-English short

```{r}
dll_eng_short <- readxl::read_excel(paste0(params$kb_dir, "/", 
                                eng_12_mo_fn), range = cell_cols("EI:HE"))

dll_eng_short_names <- stringr::str_split(string = names(dll_eng_short), pattern = "/")

dll_eng_short_names_trim <- unlist(lapply(dll_eng_short_names, `[`, 7))

# Now clean anomalous names
dll_eng_short_names_clean <- dll_eng_short_names_trim %>%
  stringr::str_replace(., " \\([a-z ]+", "") %>% # parenthetical
  stringr::str_replace(., "\\)", "") %>% # parenthetical
  stringr::str_replace_all(., ' ', '_') %>% # spaces
  stringr::str_replace_all(., "[',]", "") %>% # apostrophe
  stringr::str_replace(., "...45", "_1") %>% # ellipsis
  stringr::str_replace(., "...49", "_2") # ellipsis

names(dll_eng_short) <- dll_eng_short_names_clean
```

Let's view to confirm.

```{r}
str(dll_eng_short)
```

Now, to export, I need to concatentate the basic info.

```{r}
dll_eng_short_full <- cbind(qs_basic, dll_eng_short)
```

View again just to check.

```{r}
str(dll_eng_short_full)
```

Ok. We can do this, and it won't be too bad.

### DLL English long

```{r}
dll_eng_long <- readxl::read_excel(paste0(params$kb_dir, "/", 
                                eng_12_mo_fn), range = cell_cols("HH:KC"))

dll_eng_long_names <- stringr::str_split(string = names(dll_eng_long), pattern = "/")

dll_eng_long_names_trim <- unlist(lapply(dll_eng_long_names, `[`, 7))

# Now clean anomalous names
dll_eng_long_names_clean <- dll_eng_long_names_trim %>%
  stringr::str_replace(., " \\([a-z ]+", "") %>% # parenthetical
  stringr::str_replace(., "\\)", "") %>% # parenthetical
  stringr::str_replace_all(., ' ', '_') %>% # spaces
  stringr::str_replace_all(., "[',]", "") %>% # apostrophe
  stringr::str_replace(., "...45", "_1") %>% # ellipsis
  stringr::str_replace(., "...49", "_2") # ellipsis

names(dll_eng_long) <- dll_eng_long_names_clean
```

# 

# Post-visit notes

There is one post-hoc comments file to import.
