# Setup {-}

This section describes the setup procedure.

## Authentication {-}

The data are stored in an account on <https://kf.kobotoolbox.org>. 
The login credentials for that account are shared among the PLAY Project staff. 
To access the site's API programmatically, an API key was downloaded and added to the local `~/.Renviron` file.

<!-- https://bookdown.org/yihui/bookdown/html.html#callout-blocks -->
<!--Available blocks are: .rmdnote, .rmdcaution, .rmdimportant, .rmdtip, and .rmdwarning -->
::: {.rmdimportant}

The KoBoToolBox API key is **not** synched to GitHub.

:::


## Set-up {-}

To test whether the local system has the API key installed, we run the command `Sys.getenv("KOBO_API_KEY")`. 

### Check KoBo API Key {-}

```{r check-api-key}
kb_api <- Sys.getenv("KOBO_API_KEY")
if ((length(kb_api) != 1) || (!is.character(kb_api))) {
  stop("'KOBO_API_KEY' not installed in .Renviron")
} else {
  message("'KOBO_API_KEY' installed.")
}
```

### Check Databrary credentials {-}

The `databraryr` package handles authenticating to Databrary.
For scripting access to Databrary that require authentication, it is useful to store the user's Databrary login (email) in `.Renviron` using the R command `Sys.setenv(DATABRARY_LOGIN = "<email@provider.com>")` where you substitute your Databrary login (email) for `<email@provider.com>`.
When this has been accomplished the following code can be run to check the status of the saved variable.

```{r}
db_logon <- Sys.getenv("DATABRARY_LOGIN")
if ((length(db_logon) != 1) || (!is.character(db_logon)) || (db_logon == "")) {
  stop("'DATABRARY_LOGIN' not installed in .Renviron")
} else {
  message("'DATABRARY_LOGIN' installed.")
}
```

### Install dependencies {-}

We now use the [`renv`](https://cran.r-project.org/web/packages/renv/index.html) package to manage package dependencies.

### Load/source helper functions {-}

Most of the work is contained in `R/functions.R`.
This is sourced when we run `tar_make()` from the `{targets}` package.

::: {.rmdimportant}
We run `targets::tar_make()` manually for the time being.

None of the outputs are synced to GitHub.
:::

## Approach

To make the workflow more robust and reproducible, much of the work is embedded in functions and extensive use is made of the [`{targets}`](https://cran.r-project.org/web/packages/targets/) package. 
This document describes the workflow, but none of these code chunks are executed.

We leave execution to the `targets::tar_make()` function which updates components as needed.

:::{.rmdnote}
I am currently working on implementing most of the functions using the `box` package. This allows better isolation of dependencies within different components of the workflow.

The box-related functions are in a new `play/` directory, and the R source files are divided into categories.
The functions related to processing the screening/demographic data are in `play/screen.R`.

They will be loaded into the workspace via `box::use(play/screen)` or for modules within `play/` via `box::use(./screen)`.
:::
