# Screening call {-}

## Collection protocol {-}

Details about the data collection [protocol for participant screening and recruiting](https://www.play-project.org/collection.html#Participant_Recruitment) can be found on the [PLAY Project website](https://play-project.org).

## Retrieve from KoBoToolbox (KBT) {-}

We make use of the `targets` package for downloading data files from KoBoToolbox
and for saving local XLSX and CSV copies.
This allows us to download and process those files on a regular basis.

### Setup {-}

Load functions needed to download KBT screening/demographic questionnaire files.

```{r}
fl <- list.files(file.path(here::here(), "R"), "^kobo_|^file_", full.names = TRUE)
purrr::walk(fl, source)
```

### Download {-}

We list the screening call data files available on KBT.

```{r list-demographic-from-kbt}
(kb_screen_df <- kobo_list_data_filtered("[Dd]emographic"))
```

The following target captures this step:

```
# Not evaluated
  tar_target(
    kb_screen_df,
    kobo_list_data_filtered("[Dd]emographic"),
    cue = tarchetypes::tar_cue_age(
      name = kb_screen,
      age = as.difftime(update_interval, units = update_interval_units)
    )
  ),
```

::: {.rmdnote}

This next step could be incorporated into the `targets` workflow, but is not
as of 2023-06-23.

:::

We download and save the raw XLSX files.

```{r download-demographic-from-kbt}
kobo_retrieve_save_many_xlsx(kb_screen_df, save_dir = "../data/xlsx/screening")
```

Next, we convert the XLSX files to CSVs via a function from the `play/files` module.

```{r save-demographic-as-csv}
file_load_xlsx_save_many_csv("../data/xlsx/screening", "../data/csv/screening", "Demographic")
```

## Clean and merge {-}

### Setup {-}

A set of cleaning functions have the `screen_` prefix.

```{r}
purrr::walk(list.files(file.path(here::here(), "R"), 
                    "^screen_", full.names = TRUE), source)
```

There are three CSV files to clean:

```{r}
(fn <- list.files("../data/csv/screening", "[Dd]emographic", full.names = TRUE))
```

We clean them separately, as needed, then merge them.

### Clean variable names {-}

```{r read-screening-csvs}
df1 <-
  readr::read_csv(fn[1],
                  col_types = readr::cols(.default = 'c'),
                  show_col_types = FALSE)
df2 <-
  readr::read_csv(fn[2],
                  col_types = readr::cols(.default = 'c'),
                  show_col_types = FALSE)
df3 <-
  readr::read_csv(fn[3],
                  col_types = readr::cols(.default = 'c'),
                  show_col_types = FALSE)
```

```{r}
head(names(df1), 15)
```

```{r}
head(names(df2), 15)
```

```{r}
head(names(df3), 15)
```

There are a separate set of variable-by-variable cleaning functions in `R/screen_clean_utils.R`.

We remove the unneeded 'play_demo_*' and 'play_phone_questionnaire_' variable headers using `screen_remove_variable_headers()`.

We remove fields that contain administrative metadata with `screen_remove_metadata_fields()`.

We remove fields used only by staff in uploading data to Databrary using `screen_remove_databrary_fields()`.

We have name and address information in the screening data (e.g., '..parent_phone', '..parent_email', etc.) 

::: {.rmdnote}

In a future workflow, we will add Census FIPS IDs for the State and Country 
**before** removing the address information.

The Census queries stopped working around 2023-06-16.

For now, we remove identifiers without querying the Census.

:::

We remove identifiable information using `screen_remove_identifiers()`.

Then, we use `dplyr::full_join()` to combine the set of individually 
cleaned data files.
The `screen_clean_raw_csv()` function combines the previous `screen_remove*` functions.
The `screen_clean_raw_join()` function cleans each CSV then joins them.

```{r clean-screening-join}
(scr_df <- screen_clean_raw_join())
```

### Clean individual fields {-}

Now, we can proceed to clean-up the merged data frame.
The sequence of functions called below cleans 'construct-specific' variables
as indicated by the function names.

```{r show-screening-field-cleaning, eval=FALSE}
scr_df <- scr_df |> 
    screen_clean_child_info() |>
    screen_clean_lang_info() |>
    screen_clean_mom_info() |>
    screen_clean_biodad_father_info() |>
    screen_clean_childcare_info() |>
    screen_clean_family_structure() |>
    screen_clean_play_id() |>
    screen_remove_selected_cols() |>
    screen_select_reorder_cols()
```

For convenience, we package this sequence in its own function, `screen_clean_fields()`.

::: {.rmdnote}

Note that all of the variables are considered character strings. The `tidyverse`
suite does a great job of guessing what variables are what, but sometimes it
guesses wrongly. So, in preliminary stages, it has proved easier to make everything
a character string.

:::

```{r clean-merged-screen-fields}
scr_df <- screen_clean_fields(scr_df)
str(scr_df)
```

There is more work to do, but we have a version worth exporting.

## Export cleaned file {-}

We date-stamp the exported file so we can monitor progress as this workflow develops.

```{r export-screen}
sfn <- paste0("PLAY-screening-", Sys.Date(), ".csv")
readr::write_csv(scr_df, file.path(here::here(), "data/csv/screening/agg/", sfn))
```
