# MB-CDI {-}

## Purpose

This page documents the cleaning and merging procedures related to the MB-CDI data.
The home visit workflow strips these files into their own set of CSVs under `data/csv/home_visit/mbcdi`.

## Preparation

```{r}
source(file.path(here::here(), "R", "_OLD", "functions.R"))
```


Let's investigate the number of files, records, and variables per file.

```{r}
mbcdi_fns <-
  list.files(file.path(here::here(), "data", "csv", "home_visit", "mbcdi"), "\\.csv$", full.names = TRUE)

length(mbcdi_fns)
```

```{r make_datafile_summary}
make_datafile_summary <- function(csv) {
  assertthat::is.string(csv)
  assertthat::is.readable(csv)
  
  df <-
    readr::read_csv(csv,
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)
  
  
  
  data.frame(fn = csv,
             age_group = extract_age_group_from_name(csv),
             lang_cond = form_language(csv),
             n_subs = dim(df)[1],
             n_vars = dim(df)[2])
}
```

```{r mbcdi-file-rpt}
mbcdi_file_dat <-
  purrr::map(mbcdi_fns, make_datafile_summary) |> purrr::list_rbind()

mbcdi_file_dat |>
  dplyr::arrange(age_group, lang_cond, n_subs) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_classic()
```

## 12-mo-old English speakers

For simplicity, we'll start with the youngest age group, and with the English speakers.
There are $n=3$ forms, with 4, 10, and 111 participants each, and 254, 253, and 257 variables.
Just for fun, let's try to bind them.

```{r}
eng_12_files <- mbcdi_file_dat |>
  dplyr::filter(age_group == '12', lang_cond == 'english', n_subs > 0)

eng_12_331 <- readr::read_csv(eng_12_files$fn[1],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_331)
```

Let's try trimming the metadata labels.

```{r}
eng_12_331_trim_names <- 
  names(eng_12_331) |> basename()
eng_12_331_trim_names
```

That looks better.
Let's look at the second file.

```{r}
eng_12_363 <- readr::read_csv(eng_12_files$fn[2],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_363) |> basename()
```

And the third one.

```{r}
eng_12_740625 <- readr::read_csv(eng_12_files$fn[3],
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)

names(eng_12_740625) |> basename()
```

Now, we'll create a function to clean the variable names.

```{r}
select_basename <- function(csv_fn) {
  assertthat::is.string(csv_fn)
  assertthat::is.readable(csv_fn)
  
  df <- readr::read_csv(csv_fn,
                    col_types = readr::cols(.default = 'c'),
                    show_col_types = FALSE)
  
  names(df) <- basename(names(df))
  df
}
```

```{r}
select_basename(eng_12_files$fn[3])
```

Let's trim unneeded fields.

```{r}
trim_cdi_fields <- function(df) {
  df |>
    dplyr::select(-contains("note"),
                  -contains("instructions"),
                  -contains("comments"),
                  -contains("continue"))
}

add_particip_index <- function(df) {
  df |> 
    dplyr::mutate(play_i = 1:dim(df)[1])
}

make_cdi_longer <- function(df) {
  n_vars <- dim(df)[2]
  df |>
    tidyr::pivot_longer(cols = 2:n_vars,
                        names_to = "word",
                        values_to = "understands_or_says") |>
    dplyr::filter(!is.na(understands_or_says)) |>
    # dplyr::mutate(
    #   understands_or_says = stringr::str_replace(understands_or_says, "understands[_]+", "says")
    # ) |>
    # dplyr::mutate(understands_or_says, stringr::str_replace(understands_or_says, "sayssays", "says")) |>
    dplyr::mutate(word = stringr::str_replace(word, "mommy_001", "mommy")) |>
    dplyr::mutate(word = stringr::str_replace(word, "bath_001", "bath"))
}
```



```{r}
clean_cdi <- function(csv_fn) {
  select_basename(csv_fn) |>
    trim_cdi_fields() |>
    dplyr::rename("play_id" = "participant_id") |>
    make_cdi_longer() |>
    add_particip_index()
}
```

```{r}
eng_12_1 <- clean_cdi(eng_12_files$fn[1])
xtabs(~ word + understands_or_says, eng_12_1)
```

```{r}
eng_12_2 <- clean_cdi(eng_12_files$fn[2])
xtabs(~ word + understands_or_says, eng_12_2)
```

```{r}
eng_12_3 <- clean_cdi(eng_12_files$fn[3])
xtabs(~ word + understands_or_says, eng_12_3)
```