# Screening visualizations {-}

These visualizations are intended as a way to test the integrity and utility of the data export and cleaning workflow.

## Setup {-}

```{r load-viz-pkgs}
library(targets)
library(tidyverse)
library(forcats)
```

## Screening/recruiting calls data {-}

Cumulative screening/recruiting calls by site.

```{r load-screening-df}
targets::tar_load(screen_df, store="../_targets")
df <- add_n_calls_to_demog(screen_df)
```

### Calls across time {-}

```{r fig-screening-calls-cum, fig.cap="Cumulative screening calls by year and site"}
plot_call_timeseries(df)
```

### Calls by site {-}

```{r fig-screening-calls-by-site, fig.cap="Cumulative screening calls by site"}
calls_by_site_plot <- function(df) {
  require(dplyr)
  df %>%
    filter(., !is.na(site_id)) %>%
    ggplot(.) +
    aes(fct_infreq(site_id), fill = site_id) +
    geom_bar() +
    theme(axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
    )) + # Rotate text
    labs(x = "site") +
    theme(legend.position = "none")
}

calls_by_site_plot(screen_df)
```

### Demographics {-}

#### Child age {-}

Child age in months (`child_age_mos`) by `child_sex`.

```{r fig-age-hist-screening, fig.cap="Histogram of child age at time of recruiting call."}
screen_df %>%
  dplyr::filter(.,!is.na(child_age_mos),!is.na(child_sex)) %>%
  ggplot() +
  aes(child_age_mos, fill = child_sex) +
  geom_histogram(bins = 50)
```

::: {.rmdnote}

Some of the code to clean the `screen_df` variables could be incorporated into an earlier stage of the workflow.

:::

#### Language to child {-}

Language(s) spoken to child by `child_sex`.

```{r xtabs-language-by-sex}
df <- screen_df %>%
  dplyr::mutate(.,
                language_to_child = stringr::str_replace_all(language_to_child, " ", "_"),
                language_spoken_home = stringr::str_replace_all(language_spoken_home, " ", "_"))
xtabs(formula = ~ child_sex + language_to_child,
      data = df)
```
#### Language spoken at home {-}

```{r xtabs-language-at-home-by-sex}
xtabs(formula = ~ child_sex + language_spoken_home, data = df)
```

#### To child vs. at home {-}

```{r}
xtabs(formula = ~ language_to_child + language_spoken_home, data = df)
```

#### Child born on due date {-}

```{r}
xtabs(formula = ~ child_sex + child_bornonduedate,
      data = screen_df)
```

::: {.rmdnote}

There are a large number of NAs. Cross-check with the earlier version 
of the survey. It's possible that this question was not asked early-on.

:::

#### Child weight {-}

Must convert pounds and ounces to decimal pounds.

```{r}
df <- screen_df %>%
  dplyr::mutate(.,
                birth_weight_lbs = child_weight_pounds + child_weight_ounces/16)

df |>
  dplyr::filter(!is.na(birth_weight_lbs), !is.na(child_sex)) |>
  dplyr::filter(birth_weight_lbs > 0) |>
  ggplot() +
  aes(x = birth_weight_lbs, fill = child_sex) +
  geom_histogram(binwidth = 0.33) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

#### Birth complications {-}

```{r}
xtabs(formula = ~ child_sex + child_birth_complications,
      data = screen_df)
```

#### Major illnesses or injuries {-}

```{r}
xtabs(formula = ~ child_sex + major_illnesses_injuries,
      data = screen_df)
```

##### Child sleep {-}

##### Bed time {-}

##### Wake time {-}

##### Duration {-}

::: {.rmdimportant}

This is work yet-to-be-done. The time stamps need to be reformatted prior to
visualization.

:::

##### Nap hours {-}

::: {.rmdimportant}

Some recoding must be done here to handle strings that can't easily be 
converted to numbers.

:::

```{r}
df <- screen_df |>
  dplyr::mutate(nap_hrs = as.numeric(child_nap_hours))

df |>
  dplyr::filter(!is.na(nap_hrs), !is.na(child_sex)) |>
  ggplot() +
  aes(x = nap_hrs, fill = child_sex) +
  geom_histogram(bins = 10) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

##### Sleep location {-}

```{r}
xtabs(formula = ~ child_sex + child_sleep_location,
      data = screen_df)
```

#### Mother {-}

##### Age at childbirth {-}

```{r}
screen_df |>
  dplyr::filter(!is.na(mother_childbirth_age), !is.na(child_sex)) |>
  ggplot() +
  aes(x = mother_childbirth_age, fill = child_sex) +
  geom_histogram(bins = 25) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

Clearly, there are some impossible (erroneous) maternal ages > 100. Here are details:

```{r}
old_moms <- screen_df |>
  dplyr::filter(mother_childbirth_age > 100)

old_moms |>
  dplyr::select(submit_date, site_id, sub_num, mother_childbirth_age) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_classic()
```

##### Mother's race and ethnicity {-}

```{r xtabs-race-ethnicity}
df <- screen_df %>%
  dplyr::mutate(
    .,
    mother_race = dplyr::recode(
      mother_race,
      morethanone = "more_than_one",
      americanindian = "american_indian"
    ),
    mother_ethnicity = dplyr::recode(
      mother_ethnicity,
      hispanic_or_la = "hispanic",
      not_hispanic_o = "not_hispanic",
      nothispanic = "not_hispanic"
    )
  )
xtabs(formula = ~ mother_race + mother_ethnicity,
      data = df)
```

