# Screening visualizations {-}

These visualizations are intended as a way to test the integrity and utility of the data export and cleaning workflow.

## Setup {-}

```{r load-viz-pkgs}
library(targets)
library(tidyverse)
library(forcats)
```

To calculate cumulative screening/recruiting calls by site, we have to add an index variable

```{r load-screening-df, eval=FALSE}
targets::tar_load(screen_df, store="../_targets")
```

```{r}
screen_df <- readr::read_csv(file.path(here::here(), "data/csv/screening/agg/PLAY-screening-2023-06-23.csv"))
```

## Dates & times {-}

To calculate cumulative screening/recruiting calls by site, we have to add an index variable

```{r}
df <- screen_df |>
  dplyr::arrange(submit_date) %>%
  dplyr::mutate(n_calls = seq_along(submit_date))
```

### Calls across time {-}

```{r, fig.cap="Cumulative screening calls by year and site"}
df |>
    dplyr::filter(!is.na(submit_date), !is.na(n_calls), !is.na(site_id)) %>%
    ggplot() +
    aes(submit_date, n_calls, color = site_id) +
    geom_point()
```

```{r fig-screening-calls-cum, fig.cap="Cumulative screening calls by year and site", eval=FALSE}
plot_call_timeseries(df)
```

### Calls by site {-}

```{r fig-screening-calls-by-site, fig.cap="Cumulative screening calls by site"}
calls_by_site_plot <- function(df) {
  df |>
    filter(!is.na(site_id)) %>%
    ggplot() +
    aes(fct_infreq(site_id), fill = site_id) +
    geom_bar() +
    theme(axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
    )) + # Rotate text
    labs(x = "site") +
    theme(legend.position = "none")
}

calls_by_site_plot(df)
```

## Demographics {-}

### Child age {-}

Child age in months (`child_age_mos`) by `child_sex`.

```{r fig-age-hist-screening, fig.cap="Histogram of child age at time of recruiting call."}
screen_df |>
  dplyr::filter(!is.na(child_age_mos),!is.na(child_sex)) |>
  ggplot() +
  aes(child_age_mos, fill = child_sex) +
  geom_histogram(bins = 50)
```

::: {.rmdnote}

Some of the code to clean the `screen_df` variables could be incorporated into an earlier stage of the workflow.

:::

## Language {-}

### To child {-}

Language(s) spoken to child by `child_sex`.

```{r xtabs-language-by-sex}
df <- screen_df |>
  dplyr::mutate(language_spoken_child = stringr::str_replace_all(language_spoken_child, " ", "_"),
                language_spoken_home = stringr::str_replace_all(language_spoken_home, " ", "_"))
xtabs(formula = ~ child_sex + language_spoken_child,
      data = df)
```

### At home {-}

```{r xtabs-language-at-home-by-sex}
xtabs(formula = ~ child_sex + language_spoken_home, data = df)
```

### To child vs. at home {-}

```{r xtabs-language-child-vs-home}
xtabs(formula = ~ language_spoken_child + language_spoken_home, data = df)
```

## Child health {-}

### Child born on due date {-}

```{r xtabs-duedate}
xtabs(formula = ~ child_sex + child_bornonduedate,
      data = screen_df)
```

::: {.rmdnote}

There are a large number of NAs. Cross-check with the earlier version 
of the survey. It's possible that this question was not asked early-on.

:::

### Child weight {-}

Must convert pounds and ounces to decimal pounds.

```{r fig-birthwt-hist}
df <- screen_df %>%
  dplyr::mutate(.,
                birth_weight_lbs = child_weight_pounds + child_weight_ounces/16)

df |>
  dplyr::filter(!is.na(birth_weight_lbs), !is.na(child_sex)) |>
  dplyr::filter(birth_weight_lbs > 0) |>
  ggplot() +
  aes(x = birth_weight_lbs, fill = child_sex) +
  geom_histogram(binwidth = 0.33) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

### Birth complications {-}

```{r xtabs-birth-compl}
xtabs(formula = ~ child_sex + child_birth_complications,
      data = screen_df)
```
```{r table-birth-compl}
screen_df |>
  dplyr::filter(!is.na(child_birth_complications_specify)) |>
  dplyr::select(child_age_mos, child_sex, child_birth_complications_specify) |>
  dplyr::arrange(child_age_mos) |>
  knitr::kable(format = 'html')
```

### Major illnesses or injuries {-}

```{r xtabs-illness-injuries}
xtabs(formula = ~ child_sex + child_major_illnesses_injuries,
      data = screen_df)
```
```{r table-illness-injuries}
screen_df |>
  dplyr::filter(!is.na(child_illnesses_injuries_specify),
                !stringr::str_detect(child_illnesses_injuries_specify, "OK")) |>
  dplyr::select(child_age_mos, child_sex, child_illnesses_injuries_specify) |>
  dplyr::arrange(child_age_mos) |>
  knitr::kable(format = 'html')
```

### Child vision {-}

```{r xtabs-vision}
xtabs(formula = ~ child_sex + child_vision_disabilities,
      data = screen_df)
```

```{r table-vision}
screen_df |>
  dplyr::filter(!is.na(child_vision_disabilities_specify)) |>
  dplyr::select(child_age_mos, child_sex, child_vision_disabilities_specify) |>
  dplyr::arrange(child_age_mos) |>
  knitr::kable(format = 'html')
```

### Child hearing {-}

```{r xtabs-hearing}
xtabs(formula = ~ child_sex + child_hearing_disabilities,
      data = screen_df)
```

```{r table-hearing}
screen_df |>
  dplyr::filter(!is.na(child_hearing_disabilities_specify)) |>
  dplyr::select(child_age_mos, child_sex, child_hearing_disabilities_specify) |>
  dplyr::arrange(child_age_mos) |>
  knitr::kable(format = 'html')
```

### Child developmental delays {-}

```{r xtabs-dev-delays}
xtabs(formula = ~ child_sex + child_developmentaldelays,
      data = screen_df)
```

```{r table-dev-delays}
screen_df |>
  dplyr::filter(!is.na(child_developmentaldelays_specify)) |>
  dplyr::select(child_age_mos, child_sex, child_developmentaldelays_specify) |>
  dplyr::arrange(child_age_mos) |>
  knitr::kable(format = 'html')
```

### Child sleep {-}

::: {.rmdimportant}

This is work yet-to-be-done. The time stamps need to be reformatted prior to
visualization.

:::

#### Bed time {-}


```{r fig-bed-time-hist}
extract_sleep_hr <- function(t) {
  t |>
    stringr::str_extract("^[0-9]{2}\\:[0-9]{2}\\:[0-9]{2}") |>
    hms::as_hms()
}

df <- screen_df |>
  dplyr::mutate(child_sleep_time = extract_sleep_hr(child_sleep_time)) |>
  dplyr::filter(!is.na(child_sleep_time)) 

df |>
  dplyr::filter(!is.na(child_sleep_time),
                !is.na(child_sex)) |>
  ggplot() +
  aes(child_sleep_time, fill = child_sex) +
  geom_histogram(bins = 18) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

Some of the bed times are probably not in correct 24 hr time.

```{r}
df |>
  dplyr::filter(child_sleep_time < hms::as_hms("16:00:00")) |>
  dplyr::select(site_id, subject_number, child_sleep_time) |>
  dplyr::arrange(site_id, subject_number) |>
  knitr::kable('html')
```

#### Wake time {-}

```{r fig-wake-time-hist}
df <- screen_df |>
  dplyr::mutate(child_wake_time = extract_sleep_hr(child_wake_time)) |>
  dplyr::filter(!is.na(child_wake_time)) 

df |>
  dplyr::filter(!is.na(child_wake_time),
                !is.na(child_sex)) |>
  ggplot() +
  aes(child_wake_time, fill = child_sex) +
  geom_histogram(bins = 18) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

There are some unusual wake times, too.

```{r table-wake-time}
df |>
  dplyr::filter(child_wake_time > hms::as_hms("16:00:00")) |>
  dplyr::select(site_id, subject_number, child_wake_time) |>
  dplyr::arrange(site_id, subject_number) |>
  knitr::kable('html')
```

#### Sleep duration {-}

```{r fig-sleep-dur-hist}
df <- screen_df |>
  dplyr::mutate(child_sleep_time = extract_sleep_hr(child_sleep_time),
                  child_wake_time = extract_sleep_hr(child_wake_time)) |>
  dplyr::filter(!is.na(child_sleep_time),
                !is.na(child_wake_time)) |>
  dplyr::mutate(child_sleep_secs = (child_sleep_time - child_wake_time))

df |>
  dplyr::filter(!is.na(child_sleep_secs)) |>
  ggplot() +
  aes(child_sleep_secs, fill = child_sex) +
  geom_histogram(bins = 18) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

Again, there are some unusual values.

```{r table-sleep-dur}
df |>
  dplyr::filter(child_sleep_secs < 12000) |>
  dplyr::select(site_id, subject_number, child_sleep_time, child_wake_time, child_sleep_secs) |>
  dplyr::arrange(site_id, subject_number) |>
  knitr::kable('html')
```

#### Nap hours {-}

```{r fig-nap-hrs-hist}
df <- screen_df |>
  dplyr::mutate(child_nap_hours = as.numeric(child_nap_hours)) |>
  dplyr::filter(!is.na(child_sleep_time)) 

df |>
  dplyr::filter(!is.na(child_nap_hours),
                !is.na(child_sex)) |>
  ggplot() +
  aes(child_nap_hours, fill = child_sex) +
  geom_histogram(bins = 18) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

And there are some very long nappers or null values we need to capture.

```{r table-nap-hrs}
df |>
  dplyr::filter(child_nap_hours > 5) |>
  dplyr::select(site_id, subject_number, child_nap_hours) |>
  dplyr::arrange(site_id, subject_number) |>
  knitr::kable('html')
```


#### Sleep location {-}

```{r, eval=FALSE}
xtabs(formula = ~ child_sex + child_sleep_location,
      data = screen_df)
```

## Mother {-}

### Biological or adoptive {-}

```{r xtabs-mom-bio}
xtabs(formula = ~ child_sex + mom_bio,
      data = screen_df)
```

### Age at childbirth {-}

```{r fig-mom-age-childbirth}
screen_df |>
  dplyr::filter(!is.na(mom_childbirth_age), !is.na(child_sex)) |>
  ggplot() +
  aes(x = mom_childbirth_age, fill = child_sex) +
  geom_histogram(bins = 25) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

Clearly, there are some impossible (erroneous) maternal ages > 100. Here are details:

```{r table-mom-childbirth}
old_moms <- screen_df |>
  dplyr::filter(mom_childbirth_age > 55)

old_moms |>
  dplyr::select(submit_date, site_id, subject_number, mom_childbirth_age) |>
  knitr::kable(format = 'html')
```

### Birth country {-}

```{r xtabs-mom-birth-country}
df <- screen_df |>
  dplyr::mutate(mom_birth_country = dplyr::recode(
    mom_birth_country, 
    unitedstates = "US",
    united_states = "US",
    othercountry = "Other",
    other_country = "Other",
    refused = "Refused"
  ))

xtabs(~ mom_birth_country, data = df)
```

```{r table-mom-birth-country-non-us}
df <- screen_df |>
  dplyr::mutate(mom_birth_country_specify = stringr::str_to_title(mom_birth_country_specify)) |>
  dplyr::filter(!is.na(mom_birth_country_specify)) |>
  dplyr::select(child_sex, mom_birth_country_specify)

unique(df$mom_birth_country_specify)
```

### Education {-}

```{r xtabs-mom-educ}
df <- screen_df |>
  dplyr::filter(!is.na(mom_education)) |>
  dplyr::select(child_sex, mom_education)

xtabs(~ mom_education, data = df)
```

::: {.rmdnote}

This requires some recoding work.

:::

### Employment {-}

```{r xtabs-mom-employ}
df <- screen_df |>
  dplyr::filter(!is.na(mom_employment))

xtabs(~ mom_employment, data = df)
```

### Occupation {-}

This information is available, but would need to be substantially recoded to be useful in summary form.

### Jobs number {-}

```{r xtabs-mom-jobs-number}
df <- screen_df |>
  dplyr::filter(!is.na(mom_jobs_number))

xtabs(~ mom_jobs_number, data = df)
```

```{r xtabs-mom-jobs-vs-employ}
df <- screen_df |>
  dplyr::filter(!is.na(mom_jobs_number),
                !is.na(mom_employment))

xtabs(~ mom_jobs_number + mom_employment, data = df)
```

### Race and ethnicity {-}

```{r xtabs-race-ethnicity}
# df <- screen_df %>%
#   dplyr::mutate(
#     .,
#     mom_race = dplyr::recode(
#       mom_race,
#       morethanone = "more_than_one",
#       americanindian = "american_indian"
#     ),
#     mother_ethnicity = dplyr::recode(
#       mother_ethnicity,
#       hispanic_or_la = "hispanic",
#       not_hispanic_o = "not_hispanic",
#       nothispanic = "not_hispanic"
#     )
#   )
# xtabs(formula = ~ mother_race + mother_ethnicity,
#       data = df)
```

## Childcare {-}

### Types {-}

```{r xtabs-childcare-types}
df <- screen_df |>
  dplyr::filter(!is.na(childcare_types))
                
xtabs(~ childcare_types, data = df)
```
::: {.rmdnote}

This requires some cleaning.

:::

### Hours {-}

```{r childcare-hrs}
df <- screen_df |>
  dplyr::filter(!is.na(childcare_hours)) |>
  dplyr::arrange(childcare_hours)

unique(df$childcare_hours)
```

::: {.rmdnote}

This requires some cleaning.

:::

### Language {-}

```{r child-care-language}
df <- screen_df |>
  dplyr::filter(!is.na(childcare_language))

unique(df$childcare_language)
```

::: {.rmdnote}

This requires some cleaning.

:::
