# Demographics visualizations {-}

```{r}
if (!('home_visit_df' %in% ls())) {
  targets::tar_load(home_visit_df, store="../_targets")
}
```

## Child age {-}

Child age in months (`age_group`) by `child_sex`.

Note: The child's exact age in months is part of the Databrary-related data. 
That is on the work plan.

```{r filter-home-visit}
home_visit_filtered <- home_visit_df |>
  dplyr::filter(!is.na(age_group),!is.na(child_sex))
```

```{r}
xtabs(formula = ~ age_group + child_sex, data = home_visit_filtered)
```
A total of $n=$ `r dim(home_visit_filtered)[1]` mother-infant dyads have been tested.
This includes training and pilot visits.

```{r fig-age-grp-by-sex, fig.cap="Participants by age group and sex"}
home_visit_filtered |>
  ggplot() +
  aes(age_group, fill = child_sex) +
  geom_bar() +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())
```

## Time series {-}

To calculate cumulative visits, we have to add an index variable

```{r}
df <- home_visit_filtered |>
  dplyr::select(test_date, site_id) |>
  dplyr::mutate(test_date = as.Date(test_date)) |>
  dplyr::arrange(test_date) |>
  dplyr::mutate(n_calls = seq_along(test_date))
```

```{r fig-home-visit-time-series, fig.cap="Cumulative home visits by year"}
df |>
    dplyr::filter(!is.na(test_date), !is.na(n_calls), !is.na(site_id)) |>
    ggplot() +
    aes(test_date, n_calls) +
    geom_point()
```
