# Language visualizations {-}

```{r}
if (!('home_visit_df' %in% ls())) {
  targets::tar_load(home_visit_df, store="../_targets")
}
```

## Language exposure {-}

```{r clean-lang-df}
df <- home_visit_df |>
  dplyr::mutate(language_child = stringr::str_replace_all(language_child, " ", "_"))
xtabs(formula = ~ child_sex + language_child, data = df)
```

## MB-CDI {-}

### 12-mo-old English speakers {-}

```{r}
eng_12 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_12_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )
```

There are $n=$ `r (n_12_eng <- dim(eng_12)[1])` participant records.

```{r mcdi-12-english}
eng_12_long <- eng_12 |>
  tidyr::pivot_longer(cols = !play_id,
                        names_to = "word",
                        values_to = "understands_or_says")

#xtabs(~ word + understands_or_says, eng_12_long)
```

```{r 12-eng-wordcloud}
word_ct <- eng_12_long |>
  dplyr::filter(!is.na(understands_or_says)) |>
  dplyr::filter(understands_or_says == "understands") |>
  dplyr::count(word, sort = TRUE)

quant_25 <- round(n_12_eng*.25, 0)

wordcloud::wordcloud(words = word_ct$word, freq = word_ct$n, min.freq = quant_25)
```

### 18-mo-old English speakers {-}

```{r}
eng_18 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_18_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )

```

There are $n=$ `r (n_18_eng <- dim(eng_18)[1])` participant records.

```{r 18-eng-wordcloud}
word_ct <- eng_18_long <- eng_18 |>
  tidyr::pivot_longer(cols = !play_id,
                        names_to = "word",
                        values_to = "says") |>
  dplyr::filter(!is.na(says)) |>
  dplyr::filter(says == TRUE) |>
  dplyr::count(word, sort = TRUE)

quant_25 <- round(n_18_eng*.25, 0)

wordcloud::wordcloud(words = word_ct$word, freq = word_ct$n, min.freq = quant_25)
```

### 24-mo-old English speakers {-}

```{r}
eng_24 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_24_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )
```

There are $n=$ `r dim(eng_24)[1]` participant records.

```{r mcdi-24-english}
word_ct <- eng_24_long <- eng_24 |>
  tidyr::pivot_longer(cols = !play_id,
                        names_to = "word",
                        values_to = "says") |>
  dplyr::filter(!is.na(says)) |>
  dplyr::filter(says == TRUE) |>
  dplyr::count(word, sort = TRUE)

n_24_eng <- dim(eng_24)[1]
```

```{r mcdi-24-eng-common-words-cloud}
common_word_ct <- word_ct |>
  dplyr::filter(n < n_24_eng*.5)

wordcloud::wordcloud(words = common_word_ct$word, freq = common_word_ct$n)
```

```{r mcdi-24-eng-rare-words-cloud}
rare_word_ct <- word_ct |>
  dplyr::filter(n < n_24_eng*.25)

wordcloud::wordcloud(words = rare_word_ct$word, freq = rare_word_ct$n)
```

