# Language visualizations {-}

```{r}
if (!('home_visit_df' %in% ls())) {
  targets::tar_load(home_visit_df, store="../_targets")
}

library(wordcloud)
library(RColorBrewer)
```

## Language exposure {-}

```{r clean-lang-df}
df <- home_visit_df |>
  dplyr::mutate(language_child = stringr::str_replace_all(language_child, " ", "_"))
xtabs(formula = ~ child_sex + language_child, data = df)
```

## MB-CDI {-}

### 12-mo-old English speakers {-}

```{r}
eng_12 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_12_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )
```

There are $n=$ `r (n_12_eng <- dim(eng_12)[1])` participant records.

```{r mcdi-12-english}
eng_12_long <- eng_12 |>
  tidyr::pivot_longer(cols = !(play_id | site_id | subject_number),
                        names_to = "word",
                        values_to = "understands_or_says")

#xtabs(~ word + understands_or_says, eng_12_long)
```

```{r}
word_ct <- eng_12_long |>
  dplyr::filter(!is.na(understands_or_says)) |>
  dplyr::filter(understands_or_says == "understands") |>
  dplyr::count(word, sort = TRUE)

quant_25 <- round(n_12_eng*.25, 0)
```

```{r 12-eng-wordcloud}
# rcb_color_paired <- RColorBrewer::brewer.pal(12, 'Paired')
# wordcloud::wordcloud(words = word_ct$word, freq = word_ct$n, min.freq = quant_25, colors = rcb_color_paired)

mcdi_viz_wordcloud(word_ct, n_participants = dim(eng_12)[1], quantile = .40)
```

### 18-mo-old English speakers {-}

```{r}
eng_18 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_18_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )

```

There are $n=$ `r (n_18_eng <- dim(eng_18)[1])` participant records.

```{r}
word_ct <- eng_18 |>
  tidyr::pivot_longer(cols = !(play_id | site_id | subject_number),
                        names_to = "word",
                        values_to = "says") |>
  dplyr::filter(!is.na(says)) |>
  dplyr::filter(says == TRUE) |>
  dplyr::count(word, sort = TRUE)

quant_25 <- round(n_18_eng*.25, 0)
```

```{r 18-eng-wordcloud}
#wordcloud::wordcloud(words = word_ct$word, freq = word_ct$n, min.freq = quant_25, colors = rcb_color_paired)
mcdi_viz_wordcloud(word_ct, n_participants = dim(eng_18)[1], quantile = .50)
```

### 24-mo-old English speakers {-}

```{r}
eng_24 <-
  readr::read_csv(
    "../data/csv/home_visit/agg/mcdi_english_24_combined.csv",
    col_types = readr::cols(.default = 'c'),
    show_col_types = FALSE
  )
```

There are $n=$ `r dim(eng_24)[1]` participant records.

```{r mcdi-24-english}
word_ct <- eng_24 |>
  tidyr::pivot_longer(cols = !(play_id | site_id | subject_number),
                        names_to = "word",
                        values_to = "says") |>
  dplyr::filter(!is.na(says)) |>
  dplyr::filter(says == TRUE) |>
  dplyr::count(word, sort = TRUE)
```

```{r mcdi-24-eng-word-cloud}
mcdi_viz_wordcloud(word_ct, n_participants = dim(eng_24)[1], quantile = .60)
```

```{r mcdi-24-eng-rare-words-cloud}
rare_word_ct <- word_ct |>
  dplyr::filter(n < n_24_eng*.25)
# 
# wordcloud::wordcloud(words = rare_word_ct$word, freq = rare_word_ct$n)
mcdi_viz_wordcloud(rare_word_ct, n_participants = dim(eng_24)[1], quantile = .25)
```

