# Health visualizations {-}

```{r health-load-home-visit-df}
# Load home_visit_df if not in environment
if (!("health_df" %in% ls())) {
 targets::tar_load(health_df, store="../_targets") 
}
```

## Feeding {-}

```{r}
xtabs(formula = ~ age_group + feeding_breastfeed, data = health_df)
```

```{r fig-solid-food-mos, fig.cap="Age at introduction of solid foods"}
health_df %>%
  dplyr::select(child_sex, feeding_solidfood_age) |>
  dplyr::filter(feeding_solidfood_age < 12) |>
  ggplot() +
  aes(x = feeding_solidfood_age, color = child_sex, fill = child_sex) +
  geom_histogram(bins = 14) +
  theme(legend.title = element_blank())
```

Clearly, there are some impossible values here.

```{r anomalous-feeding}
health_df |>
  dplyr::select(participant_id, feeding_solidfood_age) |>
  
  dplyr::filter(feeding_solidfood_age > 12 | feeding_solidfood_age < 3) %>%
  knitr::kable(format = 'html')
```

A preliminary look at `feeding_comments_feeding` shows that there are some names mentioned.

::: {.rmdnote}

We should consider flagging these in the QA process.

:::

## Sleeping position {-}

These data only focus on `child_sleeping_position`.
Other sleeping data are in the screening questionnaire.

```{r}
sleeping_pos <- health_df |>
  dplyr::select(child_sex, age_group, child_sleeping_position) |>
  dplyr::filter(!is.na(child_sleeping_position))

xtabs(formula = ~ child_sleeping_position + age_group, data = sleeping_pos)
```

## Smoking/drinking {-}

```{r tab-smoking-drinking}
smoking_drinking <- health_df |>
  dplyr::select(age_group,
    child_sex,
    contains("smoking"),
    contains("drinking")
  )

xtabs(formula = ~ pregnant_smoking + pregnant_drinking, smoking_drinking)
```

```{r tab-smoking-house-car}
xtabs(formula = ~ smoking_house + smoking_car, smoking_drinking)
```

```{r tab-comments-smoking}
smoking_drinking |>
  dplyr::select(comments_smoking) |>
  dplyr::filter(!is.na(comments_smoking)) |>
  knitr::kable(format = 'html')
```

```{r tab-comments-drinking}
smoking_drinking |>
  dplyr::select(comments_drinking) |>
  dplyr::filter(!is.na(comments_drinking)) |>
  knitr::kable(format = 'html')
```

## Patient Health Questionnaire (PHQ-4) {-}

```{r fig-phq4, fig.cap="PHQ4 responses by age group and child sex"}
phq4 <- health_df |>
  dplyr::select(child_sex, age_group, contains("phq4_"))

names(phq4) <- gsub(pattern = "phq4_", 
                    replacement = "",
                    names(phq4))

phq4 |>
  tidyr::pivot_longer(!c('child_sex', 'age_group'), names_to = "question", values_to = "response") |>
  dplyr::filter(!is.na(response)) |>
  dplyr::mutate(response = factor(response,
                                  c("notatall",
                                    "severaldays",
                                    "morethanhalf",
                                    "nearly")),
                ordered = TRUE) |>
  ggplot() +
  aes(x = response, fill = child_sex) +
  geom_bar() +
  facet_grid(cols = vars(question), rows = vars(age_group)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

## Child health {-}

### Overall rating  {-}

```{r tab-child-health-rating}
child_health_rating <- health_df |>
  dplyr::select(child_sex, age_group, child_health) |>
  dplyr::filter(!is.na(child_health)) |>
  dplyr::mutate(child_health = factor(child_health,
                                      c("poor",
                                        "fair",
                                        "good",
                                        "verygood",
                                        "excellent",
                                        "donotknow",
                                        "refused"),
                                      ordered = TRUE))

xtabs(formula = ~ child_health + age_group, data = child_health_rating)
```
### Recent vaccination {-}

```{r}
recent_vax <- health_df |>
  dplyr::select(child_sex, age_group, child_vaccination) |>
  dplyr::filter(!is.na(child_vaccination))

xtabs(formula = ~ child_vaccination + age_group, data = recent_vax)
```
### Seen medical specialist {-}

```{r}
seen_specialist <- health_df |>
  dplyr::select(child_sex, age_group, child_medical_specialist) |>
  dplyr::filter(!is.na(child_medical_specialist))

xtabs(formula = ~ child_medical_specialist + age_group, data = seen_specialist)
```
::: {.rmdnote}

Manual inspection shows some possible identifying information (names) in the comments.

:::

### Illnesses and allergies {-}

```{r fig-illness-allergies}
illness_allergy <- health_df |>
  dplyr::select(child_sex, age_group, contains("illness_"))


names(illness_allergy) <- gsub(pattern = "illness_",
                               replacement = "",
                               names(illness_allergy))

illness_allergy |>
  tidyr::pivot_longer(!c('child_sex', 'age_group'),
                      names_to = "type",
                      values_to = "response") |>
  dplyr::filter(!is.na(response)) |>
  dplyr::mutate(response = factor(response,
                                  c("no", "yes", "donotknow", "refused"))) |>
  ggplot() +
  aes(x = response, fill = child_sex) +
  geom_bar() +
  facet_grid(cols = vars(type), rows = vars(age_group)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```
