# Temperament visualizations {-}

This page provides visualizations of the Early Childhood Behavior Questionnaire (ECBQ) data related to child temperament.

## Setup {-}

As of 2023-09-21, this workflow uses a separate set of functions specifically designed to extract ECBQ data from the raw KoBoToolbox files for *English-speaking families only*.

The functions are found in `R/` with the prefix `ecbq_`.

We create a "wide" data frame `ecbq_wide_df` as one of the targets of `targets:tar_make()`.
We attempt to load that here and ensure that all `R/ecbq_` functions are in the local environment.

```{r}
if (!('ecbq_wide_df' %in% ls())) {
  targets::tar_load(ecbq_wide_df, store="../_targets")
}

if (!('ecbq_plot_all' %in% ls())) {
  ecbq_fl <- list.files("../R", "^ecbq_", full.names = TRUE)
  purrr::walk(ecbq_fl, source)
}
```

## Summarize {-}

```{r}
ecbq_complete <- ecbq_wide_df |>
  tidyr::complete()

str(ecbq_complete)
```

```{r tab-ecbq-age-by-sex-cases}
xtabs(formula = ~ age_group + child_sex, ecbq_complete)
```

## Visualize {-}

For now, we just plot a few of the variables.

```{r}
ecbq_vars <- names(ecbq_complete)[stringr::str_detect(names(ecbq_complete),"rothbart_")]
```

```{r}
ecbq_plot(ecbq_complete, ecbq_vars[1])
```

```{r}
ecbq_plot(ecbq_complete, ecbq_vars[2])
```

```{r}
ecbq_plot(ecbq_complete, ecbq_vars[3])
```

```{r}
ecbq_plot(ecbq_complete, ecbq_vars[4])
```

```{r}
ecbq_plot(ecbq_complete, ecbq_vars[5])
```