# State of PLAY {-}

```{r load-packages}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(forcats))
```

The following summarizes the current state of the project as of `r (now <- ymd(Sys.Date()))`.

## Recent data {-}

```{r load-df-targets}
targets::tar_load(screen_df, store="../_targets")
targets::tar_load(home_visit_df, store="../_targets")

screen_df <- readr::read_csv(file.path(here::here(), "data/csv/screening/agg/PLAY-screening-latest.csv"))
```

### Last month {-}

#### Screening calls {-}

```{r fig-last-mo-calls}
month_ago <- now - dmonths(1)
screen_last_month_df <- screen_df %>%
  dplyr::filter(submit_date > month_ago)
```

There have been $n=$ `r dim(screen_last_month_df)[1]` recruiting calls since `r month_ago`.

```{r, fig.cap="Screening calls in last month by site"}
calls_by_site_plot(screen_last_month_df)
```

#### Home visits {-}

```{r home-visit-stats}
home_last_month_df <- home_visit_df %>%
   dplyr::filter(date_today > month_ago)
```

There have been $n=$ `r dim(home_last_month_df)[1]` home visits since `r month_ago`.

```{r fig-last-mo-home-visit, fig.cap="Home visits in last month by site"}
calls_by_site_plot(home_last_month_df)
```

### Last 3 mos {-}

#### Screening calls {-}

```{r}
three_mos_ago <- now - dmonths(3)
screen_last_3_df <- screen_df |>
   dplyr::filter(submit_date > three_mos_ago)
```

There have been $n=$ `r dim(screen_last_3_df)[1]` screening calls since `r three_mos_ago`. 

```{r fig-last-3mo-calls, fig.cap="Screening calls in last 3 months by site"}
calls_by_site_plot(screen_last_3_df)
```

#### Home visits {-}

```{r home-3mos-visit-stats}
home_last_3_month_df <- home_visit_df %>%
   dplyr::filter(date_today > three_mos_ago)
```

There have been $n=$ `r dim(home_last_3_month_df)[1]` home visits since `r three_mos_ago`.

```{r fig-last-3mo-home-visit, fig.cap="Home visits in last 3 months by site"}
calls_by_site_plot(home_last_3_month_df)
```

### Last 6 mos {-}

#### Screening calls {-}

```{r}
six_mos_ago <- now - dmonths(6)
screen_last_6_df <- screen_df |>
   dplyr::filter(submit_date > six_mos_ago)
```

There have been $n=$ `r dim(screen_last_6_df)[1]` screening calls since `r six_mos_ago`.

```{r fig-last-6mo-calls, fig.cap="Screening calls in last 6 months by site"}
calls_by_site_plot(screen_last_6_df)
```

#### Home visits {-}

```{r home-6mos-visit-stats}
home_last_6_month_df <- home_visit_df %>%
   dplyr::filter(date_today > six_mos_ago)
```

There have been $n=$ `r dim(home_last_6_month_df)[1]` home visits since `r six_mos_ago`.

```{r fig-last-6mo-home-visit, fig.cap="Home visits in last 6 months by site"}
calls_by_site_plot(home_last_6_month_df)
```

## Overall {-}

### From Databrary {-}

Because of some minor anomalies merging the older KBT surveys, we query the Databrary API for the most complete data about PLAY sessions.
For debugging purposes, we set `vb = TRUE` so we get complete information about what's working and what is not.

```{r get-session-status-from-databrary, message=FALSE, warning=FALSE}
databraryr::login_db(Sys.getenv("DATABRARY_LOGIN"))
databrary_df <- purrr::map_df(play_vols$play_site_id, make_site_session_summary, vb = TRUE) 

databrary_df %>%
  dplyr::select(., site_name, site_id, site_vol_id, PLAY_Gold, PLAY_Silver, No_Visit, `NA`) %>%
  dplyr::arrange(., desc(PLAY_Gold)) %>%
  knitr::kable(., format = 'html') 
```

### From KBT {-}

```{r load-home-visit-dataframe}
targets::tar_load(home_visit_w_databrary_df, store="../_targets")

gold_silver <- home_visit_w_databrary_df %>%
  dplyr::filter(!is.na(group_name))

xtabs(~ group_name + age_group, gold_silver)
```

```{r}
xtabs(~ group_name + child_sex, gold_silver)
```

```{r}
df_race_eth <- gold_silver %>%
  dplyr::filter(!is.na(group_name)) %>%
  dplyr::mutate(., participant_race = recode(participant_race, 
                                             `Black or African American` = "Black_or_African_American",
                                             `More than one` = "More_than_one"),
                participant_ethnicity = recode(participant_ethnicity, 
                                               `Hispanic or Latino` = "Hispanic_or_Latino",
                                               `Not Hispanic or Latino` = "Not_Hispanic_or_Latino"))

xtabs(~ participant_race + participant_ethnicity, df_race_eth)
```

### By site, location, & QA status {-}

```{r xtabs-site-qa-status}
xtabs(~ site_id + group_name, gold_silver)
```

```{r fig-qa-level-by-state, fig.cap="QA level by State"}
gold_silver %>%
    ggplot(.) +
    aes(forcats::fct_infreq(context_state), fill = context_state) +
    geom_bar() +
    facet_grid(. ~ group_name) +
    theme(axis.text.x = element_text(
      angle = 90,
      vjust = 0.5,
      hjust = 1
    )) + # Rotate text
    labs(x = "State", y = "N participants") +
    theme(legend.position = "none")
```

## Clean-up {-}

```{r clean-up}
unlink("../.databrary.RData", recursive = TRUE)
databraryr::logout_db()
```
