# Home visit: Clean variables

## Background

This page describes how the aggregate files are cleaned, measure by measure.

## Load data file

```{r}
if (!('home_visit_df' %in% ls())) {
  targets::tar_load(home_visit_df, store="../_targets")
}
```

## Remove metadata variables

```{r}
metadata_cols <- stringr::str_detect(names(home_visit_df), "note|instructions|acknowledge")

no_metadata_cols_index <- seq_along(home_visit_df)[!metadata_cols]

home_visit_df_trim <- home_visit_df |>
  dplyr::select(all_of(no_metadata_cols_index)) |>
  dplyr::select(-start,
                -end)
```

The untrimmed data frame had `r dim(home_visit_df)[2]` variables.
The trimmed data frame has `r dim(home_visit_df_trim)[2]` variables.

## Change variable names

We change some variable names to conform with later stages of processing when we merge the KoBoToolbox data with those from the Databrary session spreadsheet.

```{r}
home_visit_df_trim <- home_visit_df_trim |>
  dplyr::rename(participant_guid = participant_id,
                participant_ID = subject_number)
```

## Language variables

The raw file contains separate variables indicating whether the child is exposed to English and Spanish at home. We leave those for now.

## Locomotion variables

```{r}
loco_admin_cols <- names(home_visit_df_trim) %in% c(
  "locomotor_milestones.date_format",
  "locomotor_milestones.calc_5mo",
  "locomotor_milestones.calc_6mo",
  "locomotor_milestones.calc_7mo",
  "locomotor_milestones.calc_8mo",
  "locomotor_milestones.calc_9mo",
  "locomotor_milestones.calc_10mo",
  "locomotor_milestones.calc_11mo",
  "locomotor_milestones.calc_12mo",
  "locomotor_milestones.calc_13mo",
  "locomotor_milestones.calc_14mo",
  "locomotor_milestones.calc_15mo",
  "locomotor_milestones.calc_16mo",
  "locomotor_milestones.who_walk.walk_onset_check",
  "locomotor_milestones.holiday1.holiday_jan",
  "locomotor_milestones.holiday1.holiday_feb",
  "locomotor_milestones.holiday1.holiday_marchapril",
  "locomotor_milestones.holiday1.holiday_may",
  "locomotor_milestones.holiday1.holiday_june",
  "locomotor_milestones.holiday1.holiday_july",
  "locomotor_milestones.holiday1.holiday_sep",
  "locomotor_milestones.holiday1.holiday_oct",
  "locomotor_milestones.holiday1.holiday_nov",
  "locomotor_milestones.holiday1.holiday_dec",
  "locomotor_milestones.holiday1.memorable_events",
  "locomotor_milestones.k_walk.k_walk_onset_check",
  "locomotor_milestones.crawl_onset.crawl_onset_check",
  "locomotor_milestones.holiday2.holiday_jan2",
  "locomotor_milestones.holiday2.holiday_feb2",
  "locomotor_milestones.holiday2.holiday_marchapril2",
  "locomotor_milestones.holiday2.holiday_may2",
  "locomotor_milestones.holiday2.holiday_june2",
  "locomotor_milestones.holiday2.holiday_july2",
  "locomotor_milestones.holiday2.holiday_sep2",
  "locomotor_milestones.holiday2.holiday_oct2",
  "locomotor_milestones.holiday2.holiday_nov2",
  "locomotor_milestones.holiday2.holiday_dec2",
  "locomotor_milestones.holiday2.memorable_events2"
)

loco_admin_index <- seq_along(home_visit_df_trim)[!loco_admin_cols]

home_visit_df_loco <- home_visit_df_trim |>
  dplyr::select(all_of(loco_admin_index)) |>
  dplyr::rename(
    walk_mos_who = locomotor_milestones.who_walk.who_walk_onset_mo,
    walk_mos_kea = locomotor_milestones.k_walk.k_walk_onset_mo,
    crawl_mos = locomotor_milestones.crawl_onset.crawl_onset_mo,
    walk_onset_date_kea = locomotor_milestones.k_walk.k_walk_onset_date,
    walk_onset_date_who = locomotor_milestones.who_walk.who_walk_onset_date,
    walk_onset_comments_who = locomotor_milestones.who_walk.comments_who_walk_onset,
    walk_onset_comments_kea = locomotor_milestones.k_walk.comments_k_walk_onset,
    crawl_onset_date = locomotor_milestones.crawl_onset.crawl_onset_date,
    crawl_onset_comments = locomotor_milestones.crawl_onset.comments_crawl_onset
  ) |>
  dplyr::mutate(
    walk_mos_who = as.numeric(walk_mos_who),
    walk_mos_kea = as.numeric(walk_mos_kea),
    crawl_mos = as.numeric(crawl_mos)
  )
```

## Health variables

```{r}
health_admin_cols <- names(home_visit_df_loco) %in% c('instructions',
                                                      'note',
                                                      'doctor_told_you')

health_admin_index <- seq_along(home_visit_df_loco)[!health_admin_cols]

home_visit_df_health <- home_visit_df_loco |>
   dplyr::select(all_of(health_admin_index)) |>
  dplyr::rename(
    feeding_breastfeed = health.feeding_nutrition.breastfeed,
    feeding_solidfood_age = health.feeding_nutrition.solidfood_age,
    feeding_comments = health.feeding_nutrition.comments_feeding,
    child_sleeping_position = health.general_health.child_sleeping_position,
    child_health = health.general_health.child_health,
    child_recent_vaccination = health.general_health.child_vaccination,
    child_medical_specialist = health.general_health.child_medical_specialist,
    child_medical_specialist_comments = health.general_health.comments_child_medical_special,
    child_hearing_tested = health.general_health.child_hearing_tested,
    child_vision_tested = health.general_health.child_vision_tested,
    child_allergies = health.general_health.child_allergies_infections_ill.allergies,
    child_ear_infection = health.general_health.child_allergies_infections_ill.ear_infection,
    child_asthma = health.general_health.child_allergies_infections_ill.asthma,
    child_respiratory = health.general_health.child_allergies_infections_ill.respiratory,
    child_gastrointestinal = health.general_health.child_allergies_infections_ill.gastrointestinal,
    child_allergy_illness_comments = health.general_health.comments_allergy_etc,
    child_injury_times = health.general_health.child_injury_times,
    child_injury_comments = health.general_health.comment_injury,
    child_health_comments = health.general_health.comments_general_health,
    mom_prenatal_care = health.prenatal.prenatal_care,
    mom_prenatal_care_comments = health.prenatal.comments_prenatal,
    mom_pregnant_smoking = health.smoking.pregnant_smoking,
    mom_pregnant_smoking_trimester_1 = health.smoking.smoking_trimester_1,
    mom_pregnant_smoking_trimester_2 = health.smoking.smoking_trimester_2,
    mom_pregnant_smoking_trimester_3 = health.smoking.smoking_trimester_3,
    mom_smoking_now = health.smoking.mom_smoking_now,
    mom_smoking_now_amount = health.smoking.mom_smoking_now_amount,
    smoking_house = health.smoking.smoking_house,
    smoking_car = health.smoking.smoking_car,
    smoking_comments = health.smoking.comments_smoking,
    mom_pregnant_drinking = health.drinking.pregnant_drinking,
    mom_drinking_trimester_1 = health.drinking.drinking_trimester_1,
    mom_drinking_trimester_2 = health.drinking.drinking_trimester_2,
    mom_drinking_trimester_3 = health.drinking.drinking_trimester_3,
    mom_drinking_comments = health.drinking.comments_drinking,
    phq4_nervous = health.phq4.phq4_nervous,
    phq4_worrying = health.phq4.phq4_worrying,
    phq4_littleinterest = health.phq4.phq4_littleinterest,
    phq4_down = health.phq4.phq4_down,
    phq4_comments = health.phq4.comments_phq4
  ) |>
  # Remove duplicating variables
  dplyr::select(-health.general_health.child_hearing_tested.birthhospital,
                -health.general_health.child_hearing_tested.afterhome,
                -health.general_health.child_hearing_tested.no,
                -health.general_health.child_hearing_tested.refused,
                -health.general_health.child_hearing_tested.donotknow,
                -health.general_health.child_vision_tested.birthhospital,
                -health.general_health.child_vision_tested.afterhome,
                -health.general_health.child_vision_tested.no,
                -health.general_health.child_vision_tested.refused,
                -health.general_health.child_vision_tested.donotknow)
```

## Rothbart ECBQ

```{r}
rothbart_vars <- stringr::str_detect(names(home_visit_df_health), 'rothbart')

new_rothbart_var_names <- stringr::str_replace(names(home_visit_df_health)[rothbart_vars], "rothbart\\.rothbartquestions\\.", "")

names(home_visit_df_health)[rothbart_vars] <- new_rothbart_var_names

home_visit_ecbq <- home_visit_df_health |>
  dplyr::rename(comments_rothbart = rothbart.comments_rothbart)
```

## Media use

```{r}
home_visit_mediause <- home_visit_ecbq |>
  dplyr::rename(mediause_home_technology = mediause.home_technology,
                mediause_technology_child_tv = mediause.technology_child_tv,
                mediause_technology_child_computer = mediause.technology_child_computer,
                mediause_technology_child_ipad = mediause.technology_child_ipad,
                mediause_technology_child_dvd = mediause.technology_child_dvd,
                mediause_technology_child_educational = mediause.technology_child_educational,
                mediause_technology_child_videogame = mediause.technology_child_videogame,
                mediause_tv_how = mediause.tv_how,
                mediause_dvd_how = mediause.dvd_how,
                mediause_computer_how = mediause.computer_how,
                mediause_ipad_how = mediause.ipad_how,
                mediause_educational_how = mediause.educational_how,
                mediause_videogame_how = mediause.videogame_how,
                mediause_tv_hrs_per_day = mediause.tv_hours_per_day,
                mediause_techuse_meals = mediause.techuse.meals,
                mediause_techuse_playtime = mediause.techuse.playtime,
                mediause_techuse_bedtime = mediause.techuse.bedtime,
                mediause_techuse_transportation = mediause.techuse.transportation,
                mediause_comments = mediause.comments_technology)
```

## Pets

```{r}
home_visit_pets <- home_visit_mediause |>
  dplyr::rename(pets_at_home = pets.pets_at_home,
                pets_types_number = pets.pets_types_number,
                pets_indoors_outdoors = pets.pets_indoors_outdoors,
                comments_pets = pets.comments_pets)

unique(home_visit_pets$pets_types_number) |> head(20)
```

## Division of labor

```{r}
home_visit_labor <- home_visit_pets
names(home_visit_labor) <- stringr::str_remove(names(home_visit_labor), "division_labor\\.") |>
  stringr::str_remove("laundry\\.") |>
  stringr::str_remove("cleaning\\.") |>
  stringr::str_remove("dishwashing\\.") |>
  stringr::str_remove("cooking\\.") |>
  stringr::str_remove("feeding\\.") |>
  stringr::str_remove("droppick\\.") |>
  stringr::str_remove("bed\\.") |>
  stringr::str_remove("disciplining\\.")

home_visit_labor <- home_visit_labor |>
  dplyr::select(-instruction_dishes)
```

## Typical day

```{r}
home_visit_clean <- home_visit_labor
names(home_visit_clean) <- stringr::str_remove(names(home_visit_clean), "typical_day\\.")
names(home_visit_clean)
```

## Save cleaned file

Save with "latest" label.

```{r}
readr::write_csv(home_visit_clean, "../data/csv/home_visit/agg/PLAY-non-mcdi-kobo-latest.csv")
```

Save with date-stamp for quality control.

```{r}
fn <- paste0("../data/csv/home_visit/agg/PLAY-non-mcdi-kobo-", Sys.Date(), ".csv")
readr::write_csv(home_visit_clean, fn)
```