# Merge files

## Background

This page describes the process of merging data files.

## Home visit with Databrary

```{mermaid}
flowchart TD
  A[Home_visit] --> C[Home_all]
  B[Databrary] --> C
```

First, we load the latest home visit CSV.

```{r}
fn <- file.path(here::here(), "data", "csv", "home_visit", "agg",
                "PLAY-non-mcdi-kobo-latest.csv")

hv <- readr::read_csv(fn,
                      col_types = readr::cols(.default = "c"),
                      show_col_types = FALSE)
```

We create a helper function for the site_session data.

```{r}
make_augmented_sess_df <- function(fn) {
  df <- readr::read_csv(fn, col_types = readr::cols(.default = "c"))
  
  this_site <- basename(fn) |>
    stringr::str_remove("\\.csv")
  
  dplyr::mutate(df, site_id = this_site)
}
```

We then map the helper function across the list of session CSVs in `data/csv/site_sessions` and combine the results into a single aggregate data frame, `db_agg`.

```{r}
f_path <- file.path(here::here(), "data", "csv", "site_sessions")
session_fl <- list.files(f_path, "\\.csv$", full.names = TRUE)

if (is.null(length(session_fl))) {
  warning("No session file data")
} else {
  db <- purrr::map(session_fl, make_augmented_sess_df)
  
  db_agg <- db |>
    purrr::list_rbind() |>
    # Omit NA in session_date
    dplyr::filter(!is.na(session_date))
  
  message(dim(db_agg)[1], " rows imported.")
}
```

Finally, we join the KoBoToolbox data with the Databrary session data.

```{r}
hv_db <- dplyr::full_join(hv,
                          db_agg,
                          by = dplyr::join_by(site_id == site_id, 
                                              participant_ID == participant_ID))
```

We export this merged file.

### Save files

Save the file in `data/csv/home_visit/agg/` with the name `PLAY-non-mcdi-kobo-db-merged-latest.csv`.

```{r}
fn <- file.path(here::here(), "data", "csv", "home_visit", "agg",
                "PLAY-non-mcdi-kobo-db-merged-latest.csv")

readr::write_csv(hv_db, fn)
```

Save with date-stamp for quality control, e.g., `PLAY-non-mcdi-db-merged-2024-09-13.csv`.

```{r}
fn <- file.path(here::here(), "data", "csv", "home_visit", "agg",
                paste0("PLAY-non-mcdi-kobo-db-merged-", Sys.Date(), ".csv"))

readr::write_csv(hv_db, fn)
```
