# Clean

::: {.callout-warning}
This page is under construction.
:::

## Background

This page describes the process of cleaning the post-visit survey data.

## Import

We import the two CSVs in `data/csv/post_visit`.

```{r import-post-visit-csvs}
fl <- list.files(file.path(here::here(), "data", "csv", "post_visit"), 
                 "\\.csv$", full.names = TRUE)

pvs <- purrr::map(fl, readr::read_csv, col_types = readr::cols(.default = "c"),
                      show_col_types = FALSE)
```

## Examine 

```{r}
names(pvs[[1]])
dim(pvs[[1]])
```

```{r}
names(pvs[[2]])
dim(pvs[[2]])
```

Most of the entries are in the second form, so we start there.

```{r}
pv <- pvs[[2]]
```

## Remove metadata variables

The following variables are metadata variables that can be removed from the dataset:

```{r}
metadata_vars <- c("start",
                   "end",
                   "__version__", 
                   "meta/instanceID",
                   "_id",
                   "_uuid",
                   "_submission_time",
                   "_index",
                   "_parent_table_name",
                   "_parent_index",
                   "_tags",
                   "_notes")
```

We omit these.

```{r}
pv <- pv |>
  dplyr::select(-metadata_vars)
```

## Remove administrative variables

Some variables are intended for project staff only.

## Clean housing checklist

The housing checklist items are in `group_postvisitnotes/group_housingchecklist`.

We select them.

```{r}
housing_checklist <- pv |>
  dplyr::select(contains("group_housingchecklist"))
```

Remove the variable header (`group_postvisitnotes/group_housingchecklist`).

```{r}
(names(housing_checklist) <- stringr::str_remove(string = names(housing_checklist), "group_postvisitnotes\\/group_housingchecklist\\/"))
```

::: {.callout-note}
Discuss further cleaning with Kasey before proceeding further.
:::
