# Screening: Data dictionary

## Background {-}

We make use of the `datadictionary` package here.

This is not a perfect solution.
Among other challenges, this package throws many warnings.
But we will use it for the time being.

::: {.callout-note}
This data dictionary workflow does _not_ include the questions that were
asked.
Adding that, and more descriptive information, is a high priority.
:::

## Load data and generate dictionary

::: {.callout-note}
This data dictionary workflow does _not_ include the questions that were
asked.
Adding that, and more descriptive information, is a high priority.
:::

```{r}
#| warning: false
#| message: false
scr_df <- readr::read_csv(paste0(here::here(), "/data/csv/screening/agg/PLAY-screening-datab-latest.csv"),
                          show_col_types = FALSE)

scr_dd <- datadictionary::create_dictionary(scr_df)

readr::write_csv(scr_dd, paste0(here::here(), "/data/csv/screening/dd/PLAY-screening-data-dictionary.csv"))
```

Here are the data this package provides:

```{r}
scr_dd |>
  kableExtra::kable() |>
  kableExtra::kable_classic()
```

## Extracting questions

An alternative approach to generating the data dictionary starts with the
questionnaire files themselves.

