# Screening

## Collection protocol {-}

Details about the data collection [protocol for participant screening and recruiting](https://www.play-project.org/collection.html#Participant_Recruitment) can be found on the [PLAY Project website](https://play-project.org).

### Setup {-}

Load functions needed to download KBT screening/demographic questionnaire files.

```{r}
fl <- list.files(file.path(here::here(), "R"), "^kobo_|^file_", full.names = TRUE)
purrr::walk(fl, source)
```

## Retrieve from KoBoToolbox (KBT) {-}

We make use of the `targets` package for downloading data files from KoBoToolbox
and for saving local XLSX and CSV copies.
This allows us to download and process those files on a regular basis.

This excerpt from `_targets.R` shows two of these 'targets':

```r
  # Download screening/demographic survey
  tar_target(
    kb_screen_df,
    kobo_list_data_filtered(kb_df, "[Dd]emographic"),
    cue = tarchetypes::tar_cue_age(
      name = kb_screen,
      age = as.difftime(update_interval, units = update_interval_units)
    )
  ),
  tar_target(
    screen_download,
    screen_download_convert(kb_screen_df, "data/xlsx/screening", "data/csv/screening"),
    cue = tarchetypes::tar_cue_age(
      name = screen_df,
      age = as.difftime(update_interval, units = update_interval_units)
    )
  ),
```

The `kb_df` data frame is input to the first target `kb_screen_df`. 
`kb_df` is generated when the following target is generated (by `kobo_list_data()`).

```r
  tar_target(
    kb_df,
    kobo_list_data(),
    cue = tarchetypes::tar_cue_age(
      name = kb_df,
      age = as.difftime(update_interval, units = update_interval_units)
    )
  ),
```

The following code shows how this works:

```{r}
library(tidyverse) # for the `magrittr` pipe `%>%`

fl <-
  list.files(
    "../R",
    "^kobo_|^file_|^screen_|^ecbq_|^health_|^databrary|^home|^make|^export|^post_visit|CONSTANTS",
    full.names = TRUE
  )
purrr::walk(fl, source)

kobo_list_data()
```


<!-- ### Download {-} -->

<!-- We have two targets specified in `_targets.R` that handle the regular downloading of screening data files. -->

<!-- First, we generate a data frame of KoBoToolbox forms that contain the screening ("Demographic") data. -->
<!-- Here is the target for that process: -->

<!-- ``` -->
<!-- # Not evaluated -->
<!--   tar_target( -->
<!--     kb_screen_df, -->
<!--     kobo_list_data_filtered("[Dd]emographic"), -->
<!--     cue = tarchetypes::tar_cue_age( -->
<!--       name = kb_screen, -->
<!--       age = as.difftime(update_interval, units = update_interval_units) -->
<!--     ) -->
<!--   ), -->
<!-- ``` -->

<!-- Then we download and save the raw XLSX files to `../data/xlsx/screening` using `kobo_retrieve_save_many_xlsx(kb_screen_df, save_dir = "../data/xlsx/screening")`. -->
<!-- Finally, we convert the XLSX files to CSVs via `file_load_xlsx_save_many_csv("../data/xlsx/screening", "../data/csv/screening", "Demographic")`. -->
<!-- The latter two steps are handled by the wrapper function `screen_download_convert(kb_screen_df, "data/xlsx/screening", "data/csv/screening")`. -->
<!-- Here is the accompanying target: -->

<!-- ``` -->
<!-- # Download screening/demographic survey -->
<!--   tar_target( -->
<!--     screen_download, -->
<!--     screen_download_convert(kb_screen_df, "data/xlsx/screening", "data/csv/screening"), -->
<!--     cue = tarchetypes::tar_cue_age( -->
<!--       name = screen_df, -->
<!--       age = as.difftime(update_interval, units = update_interval_units) -->
<!--     ) -->
<!--   ), -->
<!-- ``` -->

#### Survey questions

The form for the survey questions can be downloaded from the following URL:

<https://kf.kobotoolbox.org/api/v2/assets/aGLEqT7eRBhuPgizCQBeqA.xls>

